\documentclass[12pt]{article}


\begin{document}
\begin{center}
\textbf{\large Reply to the referees and a list of changes}
\end{center}

\medskip

We are grateful to the referee for careful reading of the manuscript and providing helpful
comments. All the comments  were respected in the revision. Accordingly, the following changes were made:

\begin{itemize}
\item  References [18] and [40] were added and cited in the Introduction, regarding the
classical notion of sufficient statistics.

\item In the proof of Lemma 2.6, a sentence was added explaining that the equality $a_1=a_2$
is obtained from strict operator convexity of $t\mapsto t^{-1}$ on $(0,\infty)$.

\item In the last sentence of Remark 4.4, it  is  specified that only positivity is
assumed in Proposition 4.3.

\item References to sections, equations and theorems were corrected.

\item Definition of the generalized $s$-number was added at the beginning of Sec. 5.1.


\item In the second paragraph of Sec. 7 (Concluding remarks), it is specified that by the
''proper form'' of conditions for equality in DPI we mean that it is stated as
reversibility (sufficiency) of the channel, in the sense of Def. 4.1. This remark is added
to distinguish our results from other equality conditions known in finite dimensions, that do
not have such a clear interpretation.

\item All typos and/or grammatical mistakes pointed out by the referee were corrected. 






\end{itemize}

Additional changes to the manuscript:

\begin{itemize}
\item The reference [16] citing previous related work is added.

\item Theorem 2.4 is restated, in the sense that the expressions holds for a larger set of
parameters, namely for $0<\alpha<1$ and all $z>0$, and for $\alpha>1$ and $z\ge \alpha/2$. 
The proof is modified to cover these larger sets. Consequently, appropriate changes in the
Introduction and in some parts of the subsequent text are made.

\item Reference [36] is updated.

\item Some further typos are corrected.

\end{itemize}


\end{document}

