\documentclass[12pt]{article}

\usepackage{hyperref}
\usepackage{amsmath, amssymb, amsthm, bm}
\usepackage[sort&compress,numbers]{natbib}
\usepackage{doi}
\usepackage[margin=0.8in]{geometry}
\usepackage[all]{xy}

%\textheight23cm \topmargin-20mm  
%\textwidth175mm  
%\oddsidemargin=0mm
%\evensidemargin=0mm
%

\usepackage{amsmath, amssymb, amsthm, mathtools}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{coro}{Corollary}
\newtheorem{prop}{Proposition}


\theoremstyle{definition}
\newtheorem{defi}{Definition}


\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

\def\blabla{blabla }
\def\perm{\mathcal S}
\def\aff{\operatorname{Aff}}
\def\lin{\operatorname{Lin}}
\def\Span{\operatorname{Span}}
\def\type{\mathrm {setting}}
\def\ii{\bm{\emptyset}}
\def\tt{\bm{0}}
\def\Le{\mathcal L}
\def\Pe{\mathcal P}
\def\Ce{\mathcal C}
\def\Ae{\mathcal A}
\def\Me{\mathcal M}
\def\Fe{\mathcal F}
\def \Tr{\mathrm{Tr}\,}
\def\Se {\mathcal S}
\def\supp{\mathrm{supp}}
\def\<{\langle\,}
\def\>{\,\rangle}
\def \BS{\mathrm{BS}}
\def \Afh{\mathrm{AfH}}
\def \Af{\mathrm{Af}}
\def \FV{\mathrm{FinVect}}
\def\bV{\mathbf V}
\def\bW{\mathbf W}
\def\bE{ E}
\def\bI{I}

\def\bX{ X}
\def\bQ{\mathbf Q}
\def\bY{ Y}
\def\bZ{Z}

\title{The AfHom and boolean functions}
\author{Anna Jen\v cov\'a}

\begin{document}

\maketitle

$\Afh$ is the subcategory of $\Af$ generated from first order objects by taking tensor
products and duals. Any first order object $X$ has the form $X=(V_X,\{\tilde a_X\}^\sim)$ where
$\tilde a_X\in V_X^*$. We have
\[
S_X=V_X,\qquad L_X=\{\tilde a_X\}^\perp.
\]
Let us pick any $a_X\in \{\tilde a_X\}^\sim$ and let us denote
\[
L_{X,0}:=\mathbb Ra_X,\quad L_{X,1}:=\{\tilde a_X\}^\perp,\quad L_{X^*,0}:=\mathbb R\tilde
a_X,\quad L_{X^*,1}:=\{a_X\}^\perp.
\]
We have the decompositions
\begin{equation}\label{eq:Ldecomp}
V_X=L_{X,0}\oplus L_{X,1},\qquad V_X^*= L_{X^*,0}\oplus L_{X^*,1}
\end{equation}
and 
\begin{equation}\label{eq:Lperp}
L_{X,0}^\perp=L_{X^*,1},\quad L_{X,1}^\perp=L_{X^*,0}.
\end{equation}

Let  $Y$ be an object of  $\Afh$. Ten $Y$ is constructed from a set of distinct first order object $X_1,\dots, X_n$.
In this case, we will write $Y\sim[X_1,\dots,X_n]$.  Since
$\FV$ is compact, 
$(V\otimes W)^*=V^*\otimes W^*$, so that the vector space of $Y$ has the form
\[
V_Y=V_{i_1}\otimes \dots\otimes V_{i_n},
\]
where $V_i$ is either $V_{X_i}$ or $V_{X_i}^*$, according to whether $X_i$ was subjected
to taking duals an even or odd number of times. The indices such that the first
case is true will be called the outputs and the subset of outputs in $[n]$ will be denoted
by $O$, or $O_Y$, when we need to specify the object. The set $I=I_Y:=[n]\setminus O_Y$ is
the set of inputs. The following statement shows the reason for this terminology.
The proof of Proposition \ref{prop:setting} will be given later below.

\begin{prop}\label{prop:setting} Let $Y\sim[X_1,\dots,
X_n]$. Let us denote  
\[
X_I:=\bigotimes_{i\in I} X_i,\qquad X_O:=\bigotimes_{i\in O} X_i.
\]
Then there is a permutation $\sigma\in S_n$ such that 
\[
X_I^*\otimes X_O\xrightarrow{\sigma} Y \xrightarrow{\sigma^{-1}} [X_I,X_O].
\]
\end{prop}


We introduce the following notations:
\[
V_i:=V_{X_i},\quad L_{i,u}:=L_{X_i,u},\quad \tilde L_{i,u}=L_{X^*_i,u},\ u\in \{0,1\}, \qquad i\in O
\]
and 
\[
V_i:=V_{X_i}^*,\quad L_{i,u}:=L_{X^*_i,u},\quad \tilde L_{i,u}=L_{X_i,u},\ u\in \{0,1\},\qquad i\in I.
\]
Further,
\[
a_i:=a_{X_i},\quad \tilde a_i:=\tilde a_{X_i},\quad i\in O,\qquad a_i:=
\tilde a_{X_i},\quad \tilde a_i:=a_{X_i},\quad i\in I.
\]
We will also denote for $s\in \{0,1\}^n$,
\[
L_s:=L_{i_1,s_{i_1}}\otimes\dots\otimes  L_{i_n,s_{i_n}},\qquad \tilde L_s:=\tilde
L_{i_1,s_{i_1}}\otimes\dots\otimes  \tilde L_{i_n,s_{i_n}}.
\]
Notice that the subspaces  $L_s$, $s\in\{0,1\}^n$ form an independent decomposition of the space
$V_Y$, so that they generate a distributive sublattice in the latice of subspaces of
$V_Y$. Similarly, $\tilde L_s$, $s\in \{0,1\}^n$ form an independent decomposition of
$V_Y^*$. 


We next describe the affine subspace $A_Y$. We will need the following easy lemmas.

\begin{lemma}\label{lemma:La} We have
\[
a_Y:=a_{i_1}\otimes \dots \otimes a_{i_n}\in A_Y,\quad \tilde a_Y:=\tilde a_{i_1}\otimes
\dots \otimes \tilde a_{i_n}\in \tilde A_Y.
\]

\end{lemma}

\begin{proof} Easy.

\end{proof}



\begin{lemma}\label{lemma:Lperp}   For any $s\in \{0,1\}^n$, we have 
\[
L_s^\perp=
\bigoplus_{\substack{t\in\{0,1\}^n\\ t\ne s}} \tilde L_t.
\]


\end{lemma}

\begin{proof} Using
\eqref{eq:Ldecomp} and \eqref{eq:Lperp}, we get
\begin{align*}
\left(L_{i_1,s_{i_1}}\otimes \dots\otimes L_{i_n,s_{i_n}}\right)^\perp&= \bigvee_j\left(
V_{i_1}^*\otimes
\dots \otimes V_{i_{j-1}}^*\otimes \tilde L_{i_j,1-s_{i_j}}\otimes V_{i_{j+1}}^*\otimes\dots \otimes
V_{i_n}^*\right)\\
&= \bigvee_j \left( \bigoplus_{\substack{t\in \{0,1\}^n\\ t_{i_j}\ne s_{i_j}}} \tilde
L_{i_1,t_{i_1}}\otimes\dots \otimes \tilde
L_{i_n,t_{i_n}}\right)\\
&= \bigoplus_{\substack{t\in \{0,1\}^n\\ t\ne s}} \left( \tilde L_{i_1,t_{i_1}}\otimes\dots \otimes \tilde
L_{i_n,t_{i_n}}\right).
\end{align*}


\end{proof}

We next show how the objects are related to some boolean functions, in fact, these
functions are related to types of objects in $\Afh$, rather than objects themselves.

\begin{theorem}\label{thm:boolean}
For any object in $\Afh$, there is a function $f=f_Y:\{0,1\}^n\to \{0,1\}$ 
and a permutation $i_1,\dots,i_n$ of elements in $[n]$,  
such that 
\[
S_Y=\bigoplus_{s\in \{0,1\}^n} f(s) L_{i_1,s_{i_1}}\otimes\dots\otimes
L_{i_n,s_{i_n}}.
\]


\end{theorem}

\begin{proof} We will proceed by induction on $n$. For $n=1$, the assertion is easily seen
to be true, since in this case, $Y$ is itself first order and
\[
S_Y=V_Y=L_{1,0}\oplus L_{1,1}=f(0)L_{1,0}\oplus f(1)L_{1,1},
\]
here $f:\{0,1\}\to \{0,1\}$ is the constant 1. Assume now that the assertion is true for
all $m<n$. By construction, $Y$ is either the tensor product of two other objects in
$\Afh$ or $Y$ is the dual of such a product. Let us assume the first case. Then there is a
permutation $i_1,\dots, i_n$ of $[n]$ and $0<m<n$  such that $Y=Y_1\otimes Y_2$, with
\[
Y_1\sim [X_{i_1},\dots, X_{i_m}],\qquad Y_2\sim[X_{i_{m+1}},\dots, X_{i_n}].
\]
  By the
assumption, there are functions $f_1:\{0,1\}^{m}\to \{0,1\}$ and $f_2:\{0,1\}^{n-m}\to
\{0,1\}$, and permutations $k_1,\dots, k_m$ of $[m]$, $l_1,\dots,l_{n-m}$ of $[n-m]$
such that
\[
S_Y=S_{Y_1}\otimes S_{Y_2}=\bigoplus_{\substack{s\in\{0,1\}^{m}\\ t\in
\{0,1\}^{n-m}}}
f_1(s)f_2(t)L_{i_{k_1},s_{k_1}}\otimes\dots \otimes L_{i_{k_m},s_{k_m}}\otimes
L_{i_{m+l_1},t_{l_1}}\otimes\dots\otimes L_{i_{m+l_{n-m}},t_{l_{n-m}}}
\]
Since $\{0,1\}^n\simeq \{0,1\}^m\times \{0,1\}^{n-m}$, we get the assertion, with
$f(s,t)=f_1(s)f_2(t)$ and the permutation
$i_{k_1},\dots,i_{k_m},i_{m+l_1},\dots,i_{m+l_{n-m}}$ of $[n]$.

To finish the proof, it is now enough to observe that if the assertion holds for $Y$ then
it also  holds for $Y^*$. So assume that $Y$ has the required form. 
Let $a_Y$ and $\tilde a_Y$ be as in  Lemma \ref{lemma:La}, then $\tilde a_Y\in \tilde
A_Y$, so that $L_Y=S_Y\cap\{\tilde a_Y\}^\perp$. 
As before, we use the notation
\[
L_s:=L_{i_1,s_{i_1}}\otimes\dots\otimes  L_{i_n,s_{i_n}},\qquad \tilde L_s:=\tilde
L_{i_1,s_{i_1}}\otimes\dots\otimes  \tilde L_{i_n,s_{i_n}}.
\]
respecting the permutation $i_1,\dots,i_n$ of $Y$, so that
\[
S_Y=\bigoplus_{s\in\{0,1\}^n}f(s)L_s.
\]
It is easily seen that for any $s\in
\{0,1\}^n$, $L_s\subseteq \{\tilde a_Y\}^\perp$ if and only if $s_i=1$ for at least some $i\in [n]$,
that is, $s\ne 00\dots0$. Hence
\[
L_Y=\bigoplus_{\substack{s\in \{0,1\}^n\\ s\ne 0}} f(s) L_s.
\]
We then have using Lemma \ref{lemma:Lperp} and the fact that $\tilde L_t$, $t\in
\{0,1\}^n$ form an independent decomposition of $V_Y^*$,
\begin{align*}
S_{Y^*}&=L_Y^\perp=\left(\bigoplus_{\substack{s\in \{0,1\}^n\\ s\ne 0}}
f(s)L_s)\right)^\perp=\bigwedge_{\substack{s\in\{0,1\}^n\\ s\ne 0, f(s)=1}}L_s^\perp=
\bigwedge_{\substack{s\in\{0,1\}^n\\ s\ne 0,
f(s)=1}}\left(\bigoplus_{\substack{t\in\{0,1\}^n\\t\ne s}} \tilde L_t\right)\\
&=\bigoplus_{t\in\{0,1\}^n} \left(\bigwedge_{\substack{s\in \{0,1\}^n\\ s\ne 0, f(s)=1}}
(1-\chi_s(t))\tilde L_t\right)=\bigoplus_{t\in \{0,1\}^n} f^*(t) \tilde L_t.
\end{align*}
Here $\chi_s:\{0,1\}^n\to \{0,1\}$ is the characteristic function of $s$ and
$f^*:\{0,1\}^n\to \{0,1\}$ is given as
\[
f^*(t):=\bigwedge_{\substack{s\in \{0,1\}^n\\ s\ne 0, f(s)=1}}
(1-\chi_s(t))=\begin{dcases} 1 & \text{if } t=0\\ 1-f(t) & \text{if } t\ne 0.
\end{dcases}
\]
Note also that the change $L_s$ to $\tilde L_s$ corresponds precisely to swapping the sets
of inputs and outputs, which is what happens after taking the dual. This finishes the
proof.

\end{proof}


The above theorem shows that any element $Y\sim[X_1,\dots,X_n]$ is up to a permutation
determined by a unique boolean function $f=f_Y:\{0,1\}^n\to \{0,1\}$, uniqueness follows from
the fact that $L_s, s\in \{0,1\}^n$ form an independent decomposition of $V_Y$.
It is rather obvious that not all boolean functions give rise to an object of $\Afh$, for
example, for $Y\sim [X]$ we only have $Y=X$ and $Y=X^*$, which corresponds to constant
1 and the negation, respectively. In general, one can see from the above proof that we
necessarily have 
\[
f\in \Fe_n=\{g:\{0,1\}^n\to \{0,1\},\ g(0)=1\}.
\]
Pick  any $f\in \Fe_n$ and any permutation $i_1,\dots,i_n$. Keeping the above notations,
in particular the input-output decomposition $[n]=I\cup O$, let 
\[
S_f:=\bigoplus_{s\in \{0,1\}^n} f(s)L_s,\qquad  A_f:=S_f\cap\{\tilde a\}^\sim.
\]
Then $A_f$ is a proper affinne subspace in $V:=\otimes_{j}V_{i_j}$, this folows from the
fact that $f(0)=1$, so that $S$ contains the subspace $\mathbb R a$. 
Then $Y_f:=(\otimes_{j}V_{i_j},A_f)$ defines an object in $\Af$ such that $a\in A_f$ and
$\tilde a\in \tilde A_f$. Such objects might not belong to $\Afh$ in
general.
With the pointwise ordering, $\Fe_n$ is a distributive lattice, with the smallest element
$\chi_0$ and largest element $1$.  It is easy to see that for  $f,g\in \Fe_n$ and some
corresponding objects $Y_f$, $Y_g$, we have $f\le g$  if
and only if there is some permutation $\sigma\in S_n$ such that 
$Y_f\xrightarrow{\sigma} Y_g$. In particular, since $\chi_0\le f\le 1$ for all $f\in
\Fe_n$, there is some permutation $\sigma$ such that 
\[
Y_{\min}\xrightarrow{\sigma} Y_f\xrightarrow{\sigma^{-1}} Y_{\max},
\]
where 
\[
Y_{\min}:=(V_1\otimes\dots\otimes V_n, \{a_1\otimes\dots\otimes a_n\}),\qquad
Y_{\max}:=(V_1\otimes \dots\otimes V_n,\{\tilde a_1\otimes\dots\otimes \tilde a_n\}^\sim).
\]
If $Y_g$ is an object such that 
\[
Y_{\min}\xrightarrow{\rho} Y_g\xrightarrow{\rho^{-1}} Y_{\max},
\]
for a permutation $\rho$, then we may define an object corresponding to $f\wedge g$ as the
pullback of the two arrows $f\xrightarrow{\sigma^{-1}} Y_{\max}$ and
$g\xrightarrow{\rho^{-1}} Y_{\max}$, similarly, $Y_{f\vee g}$ can be found as a pushout.

\section{Boolean functions}



We will work with certain boolean functions, which are defined as  functions from binary
strings to $\{0,1\}$. We now list some basic notations used below.

For $s\in \{0,1\}$, we denote $\bar s:=1-s$.
For binary strings of fixed length $n$, that is, elements of
$\{0,1\}^n$, we will denote by $0_n$ or just $0$ the string $00\dots0$ and by $e^i$ the
string such that $e^i_j=\delta_{i,j}$.  For $m,n\in \mathbb N$, the concatenation of 
strings $s\in \{0,1\}^m$ and $t\in \{0,1\}^n$ will be denoted by $st$, that is,
\[
st=s_1\dots s_mt_1\dots t_n\in \{0,1\}^{m+n}.
\]
For a string $x\in \{0,1\}^n$ and any set of indices $\{i_1,\dots,i_k\}\subseteq [n]$, we
will denote by $x^{i_1\dots i_k}$ the string in $\{0,1\}^{n-k}$ obtained from $x$ by removing
$x_{i_1},\dots, x_{i_k}$.

For any permutation $\sigma\in S_n$, we will denote by the same symbol the obvious action
on $\{0,1\}^n$, that is
\[
\sigma(s_1\dots s_n)=s_{\sigma^{-1}(1)}\dots s_{\sigma^{-1}(n)}.
\]

We start by looking at the set 
\[
\Fe_n:=\{f:\{0,1\}^n\to \{0,1\},\ f(0)=1\}.
\]
With the poitwise ordering, $\Fe_n$ is  a (finite) distributive lattice, with top element
 the constant 1 function and the bottom element $p_n:=\chi_{0}$.  We may also
define complementation  in $\Fe_n$ as
\[
f^*:=1-f+p_n.
\]
It can be easily checked that with these structures $\Fe_n$ is a boolean algebra.

We now introduce some more operations in $\Fe_n$. For $f\in \Fe_n$ and any permutation $\sigma\in S_n$, we see that $f\circ \sigma\in \Fe_n$.
For $f\in \Fe_{m}$ and $g\in \Fe_n$, we define
the function $f\otimes g\in \Fe_{m+n}$ as
\[
(f\otimes g)(st)=f(s)g(t). 
\]
As it is, this tensor product is not symmetric, but there is a permutation $\sigma\in S_{m+n}$ such that 
$(g\otimes f)=(f\otimes g)\circ \sigma$ for any $f\in \Fe_m$ and $g\in \Fe_n$.

\begin{lemma}\label{lemma:fproduct} For $f\in \Fe_m$, $g\in \Fe_n$, we have
\[
f\otimes g\le (f^*\otimes g^*)^*.
\]
Equality holds if and only if $f$ and $g$ are either both the to top or both the bottom elements in
$\Fe_m$ resp. $\Fe_n$.
\end{lemma}

\begin{proof} The inequality is easily  checked, since $(f\otimes g)(st)$ can be 1 only if
$f(s)=g(t)=1$. If both $s$ and $t$ are the zero strings, then $st=0_{m+n}$ and both sides
are equal to 1. Otherwise, the condition $f(s)=g(t)=1$ implies that $(f^*\otimes
g^*)(st)=0$, which implies that the right hand side must be 1. If $f$ and $g$ are both
constant 1, then $(1\otimes 1)^*=1^*=p_{n+m}=1^*\otimes 1^*$, in the case when both $f$
and $g$ are the minimal elements equality  follows by
duality. Finally, asume the equality holds and that $f\ne 1$, so that there is some $s$ such that 
$f(s)=0$. But then $s\ne 0$ and for any $t$,
\[
0=(f\otimes g)(st)=(f^*\otimes g^*)^*(st)=1-f^*(s)g^*(t)+p_{m+n}(st)=1-g^*(t),
\]
which implies that $g(t)=0$ for all $t\ne0$, that is, $g=p_n$. By the same argument,
$f=p_m$ if $g\ne 1$, which implies that either $f=1$ and $g=1$, or $f=p_m$ and $g=p_n$.



\end{proof}



We now show an important example. 


\begin{example}\label{ex:ps} Let $S\subseteq [n]$ be any subset. We will denote
\[
p_S(s):=\prod_{i\in S}\bar s_i.
\]
It is clear that $p_S\in \Fe_n$, $p_{\emptyset}=1$, $p_{[n]}=\chi_0=p_n$. The folowing
properies are also easy
to see for $S,T\subseteq [n]$:
\begin{enumerate}
\item[(i)] if $S\subseteq T$, then $p_T\le p_S$,
\item[(ii)]  $p_S\wedge p_T=p_Sp_T=p_{S\cup T}$,
\item[(iii)]  $p_S\vee p_T=p_S+p_T-p_{S\cup T}$.
\item[(iv)] let $S\subseteq [m]$ and $T\subseteq [n]$, then 
\[
p_S\otimes p_T=p_{S\cup (m+T)}.
\]
\end{enumerate}


\end{example}




We will use the above functions to introduce  a convenient  parametrization to $\Fe_n$.  
For this, we first include $\Fe_n$ into a larger set
\[
\Fe_n\subseteq \{f:\{0,1\}^n\to \mathbb R\}=:\mathcal V,
\]
which is a $2^n$-dimensional real vector space. It becomes a Hilbert space with respect to
the inner product
\[
\<f,g\>=\sum_{s\in \{0,1\}^n} f(s)g(s). 
\]

\begin{lemma}\label{lemma:Vbasis} The set $\{p_S,\ S\subseteq [n]\}$ is a basis of
$\mathcal V$.
Any $f\in \mathcal V$ can be uniquely written as
\[
f=\sum_{S\subseteq [n]} \hat f_Sp_S,
\]
where the coefficients $\hat f_S\in \mathbb R$ are obtained as
\[
\hat f_S=\sum_{\substack{x\in \{0,1\}^n\\ x_i=1, \forall  i\in S^c}} (-1)^{\sum_{i\in
S}x_i}f(x).
\]
\end{lemma}



\begin{proof} For $T\subseteq [n]$, let us define the function $p_T^\perp$ as
\[
p_T^\perp(x):= (-1)^{\sum_{i\in T}x_i}\prod_{i\in T^c}x_i. 
\]
We prove that for $S,T\subseteq [n]$,
\[
\<p_S,p^\perp_T\>=\delta_{S,T},
\]
which shows that $\{p_S,\ S\subseteq [n]\}$ is a basis and 
$\{p_T^\perp, \ T\subseteq [n]\}$  is the dual basis. We compute
\[
\<p_S,p^\perp_T\>=\sum_x p_S(x)p^\perp_T(x)=\sum_x (-1)^{\sum_{i\in T} x_i}\prod_{i\in S}
\bar x_i\prod_{j\in T^c}x_j.
\]
This expression can be nonzero only if $S\cap T^c=\emptyset$, that is, $S\subseteq T$. In
this case, the last sum  is equal to
\[
\sum_{\substack{x\in \{0,1\}^n\\ x_i=0,\forall i\in S\\x_i=1,\forall i\in T^c}}
(-1)^{\sum_{j\in T\setminus S}x_j}=\begin{dcases} 0 & \text{if } S\subsetneq T\\
  1 &\text{if } S=T
  \end{dcases}
\]
It is now clear that the coefficients
\[
\hat f_S=\<f,p^\perp_S\>
\]
have the given form.


\end{proof}

It may be useful to visualise the lattice $\mathcal L_n=\{S\subseteq [n]\}$ as a
hypercube, and the coefficients of $f$ as labels for its vertices. The fact that the
function $f$ has values in $\{0,1\}$ means that for a string $x\in \{0,1\}^n$ such that
$x_j=1$ if and only if $j\in T$, we must have 
\[
f(x)=\sum_{\substack{S\subseteq [n]\\ S\cap T=\emptyset}} \hat f_S\in \{0,1\},
\]
that is, the sum of labels $\hat f_S$ over any face of the hypercube $\mathcal L_n$ containing the vertex $\emptyset$ must
be 0 or 1. In particular, $\hat f_\emptyset=f(11\dots 1)\in \{0,1\}$, which restricts the
values of $\hat f_{\{i\}}\in
\{0,1,-1\}$, etc. The fact that $f\in \Fe_n$ means that in addition,
\[
f(0)=\sum_{S\subseteq [n]}\hat f_S=1.
\]


\subsection{The type functions}

We are now interested in the subset  $\Fe_n^H$ in $\Fe_n$ of elements that can be 
obtained from the constant function $1$ on $\{0,1\}$ by taking complements, tensor
products and precomposing with permutations.
This gives the following description. 

\begin{defi}\label{defi:fhn} The set $\Fe_n^H$ is the smallest subset in $\Fe_n$ such
that:
\begin{enumerate}
\item it is invariant under permutations: if $f\in \Fe_n^H$, then $f\circ \sigma\in
\Fe_n^H$ for any permutation $\sigma\in S_n$,
\item it is invariant under complementation: if $f\in \Fe_n^H$ then $f^*\in \Fe_n^H$,
\item if $f\in \Fe_n^H$ and $g\in \Fe_m^H$, then $f\otimes g\in \Fe_{n+m}^H$,
\item $\Fe_1^H=\{1,\chi_0\}=\Fe_1$. 



\end{enumerate}
Elements of $\Fe_n^H$ are called type functions of order $n$.


\end{defi}


We can see by the above definiton that a type function can be constructed as 
\[
f(x_1\dots x_n)=(((1\otimes ..1\otimes 1^*\otimes 1^*)^*...)\otimes (1\otimes..1\otimes
1^*....)..)^*..)\circ
\sigma(x_1\dots x_n)
\]
where each 1 or $1^*$ acts on $\{0,1\}$ and  $\sigma$ is some permutation. This gives a
decomposition of the set of indices as follows. We say that $i\in [n]$ is an output index
for $f$ if $x_i$ in the above expression is subjected to complementation an even number of
times. The subset of such indices in $[n]$ will be denoted by $O_f$, or just $O$. We also
denote $I=I_f:=[n]\setminus O_f$, the elements of $I_f$ will be called input indices for
$f$.






\begin{example}\label{ex:psh}  Note that $p_S\in \Fe_n^H$ for any $S\subseteq [n]$. 
Indeed, we have $p_S=f_1\otimes\dots \otimes f_n$, where
$f_i=\chi_0=1^*$ if $i\in S$ and $f_i=1$ otherwise. It is clear that in this case $I=O$ is
the set of input indices.


\end{example}



\begin{prop}\label{prop:fh_setting} Let $f\in \Fe_n^H$ and let $O=O_f$,  $I=I_f$. Then
\[
p_I\le f\le p_O^*.
\]

\end{prop}

\begin{proof} This is obviously true for $n=1$. In this case,
$\Fe_1^H=\Fe_1=\{1,1^*=p_{[1]}\}$. If $f=1$, then $O=[1]$, $I=\emptyset$ and 
\[
p_I=p_{\emptyset}=1=p_O^*,
\]
the case  $f=1^*$ is obtained by taking complements. Assume that the assertion holds for
$m<n$. Let $f\in \Fe^H_n$ and assume that  $f=g\otimes h$ for some  $g\in
\Fe_m^H$, $h\in \Fe_{n-m}^H$.  By the assumption,
\[
p_{I_g}\otimes p_{I_h}\le g\otimes h\le p^*_{O_g}\otimes p^*_{O_h}\le (p_{O_1}\otimes
p_{O_2})^*,
\]
the last inequality follows from Lemma \ref{lemma:fproduct}. It is now enough to notice that 
$O_f=O_g\cup (m+O_h)$, $I_f=I_g\cup (m+I_h)$, so that $p_{O_f}=p_{O_g}\otimes p_{O_h}$ and
similarly for $p_{I_f}$. 

Assume that the inequality holds for $f\in\Fe_n^H$, we will show that it is
preserved by permutations and complements. Indeed, let $\sigma$ be any
permutation of the indices, then clearly
\[
p_I\circ\sigma\le f\circ\sigma\le p_O^*\circ\sigma.
\]
It is enough to note that the outputs of $f\circ\sigma$ are $\sigma^{-1}(O)$, similarly
for the inputs, and $p_{\sigma^{-1}(S)}=p_S\circ\sigma$ for any $S\subseteq [n]$. 
Finally, we have by duality
\[
p_O\le f^* \le p_I^*,
\]
and taking complements exchanges inputs and outputs: $O_{f^*}=I_f$, $I_{f^*}=O_f$.






\end{proof}






The next result shows that there is a direct way to obtain the input-output decomposition
from values of 
$f$.

\begin{prop}\label{prop:fh_outputs} For $f\in \Fe_n^H$, $i\in O_f$ if and only if $f(e^i)=1$. 


\end{prop}

In other words, the outputs of $f$ are precisely those indices for which the sum of the
coefficients $\hat f_S$ over the facet $\{S\in \mathcal L_n,\ i\notin S\}$ is 1.


\begin{proof} Let $i\in O_f$, then by Proposition \ref{prop:fh_setting}, $p_{I_f}(e^i)=1\le
f(e^i)$, so that $f(e^i)=1$. Conversely, if $f(e^i)=1$, then by the other inequality in
Proposition \ref{prop:fh_setting}, $p_{O_f}(e^i)=0$, whence $i\in O_f$.


\end{proof}


\begin{example}\label{ex:chain12} Let $n=2$, then it can be checked that 
\[
\Fe^H_2=\{p_2, p_{\{1\}}, p_{\{2\}}, p_{\{1\}}^*, p_{\{2\}}^*,1\}.
\]
Explicitly, the functions are given as
\[
x\mapsto   \qquad \bar x_1\bar x_2,\quad \bar x_1,\quad \bar x_2, \quad 1-\bar x_1+\bar
x_1\bar x_2,\quad 1-\bar x_2+\bar x_1\bar x_2,\quad 1.
\]
It can be seen that $\Fe_n$ has $2^{2^n-1}$ elements, so that $\Fe_2$ has 8
elements in total. The two of them that are not type functions are 
\[
g(x)=1-\bar x_1-\bar x_2+2\bar x_1x_2,\qquad g^*(x)=\bar x_1+\bar x_2-\bar x_1\bar x_2.
\]
This can be checked directly from Propositions \ref{prop:fh_setting} and
\ref{prop:fh_outputs}. Indeed, if $g\in \Fe^H_n2$, we would have $O_g=\emptyset$, so that 
$p_2\le g\le p_\emptyset^*=p_2$, which is obviously not the case. Clearly, also the
complement $g^*\notin \Fe_2^H$. Notice also that $g^*=p_{\{1\}}\vee p_{\{2\}}$, so that
$\Fe_n^H$ is a subposet in $\Fe_n$ but not a lattice.


\end{example}


\subsubsection{The poset $\mathcal P_f$}


For $f\in \Fe_n^H$, let $\mathcal P_f$ be the subposet in $\mathcal L_n$ of elements such that
$\hat f_S\ne 0$. Can we characterize such subposets? (we cannot so far.) Can we extract
some information about some 'causal structure' on the indices? 

We next give some properties such a poset must have. We say that a poset is graded of rank
$k$ if every maximal chain in $P$ has the same length equal to $k$ (recall that the length
of a chain is defined as number of its elements -1). Equivalently,  there is
a unique rank function $\rho: P\to \{0,1,\dots,k\}$ such that $\rho(s)=0$ if $s$ is a
minimal element of $P$ and $\rho(t)=\rho(s)+1$ if $t$ covers $s$. 

\begin{prop}\label{prop:graded} Let $f\in \Fe_n^H$, then $\mathcal P_f$ is a graded poset
with even rank $k\le n$. If $\rho$ is the rank function, then we have
\[
\hat f_S=(-1)^{\rho(S)},\qquad S\in \mathcal P_f.
\]

\end{prop}

Then rank of $\Pe_f$ will be denoted by $r(f)$ and called the rank of $f$.

\begin{proof} For $n=1$, we have $\mathcal L_1=\{\emptyset, [1]\}$ and
$\Fe_1^H=\{1,1^*\}$. For $f=1$, $\mathcal P_f=\{\emptyset\}$ is a singleton, which 
is clearly a graded poset, with rank $k=0$ and trivial rank function $\rho$.  We have
\[
\hat f_\emptyset = 1=(-1)^0=(-1)^{\rho(\emptyset)}.
\]
The proof for $f=1^*$ is similar.

If the statement
holds for $f$, then it holds also for $f\circ \sigma$ for any $\sigma\in S_n$, indeed,
$\widehat{f\circ \sigma}_S=\hat f_{\sigma^{-1}}(S)$ so that 
$\mathcal P_f$ and $\mathcal P_{f\circ \sigma}$ are isomorphic. For $f^*$, note that
\begin{equation}\label{eq:dual_rank}
f^*=1-f+p_n=(1-\hat f_\emptyset)1 -\sum_{\substack{S\in \mathcal P_f\\ \emptyset \ne S,
[n]\ne S}}
(-1)^{\rho(S)}+(1- \hat f_{[n]})p_n.
\end{equation}

If $\emptyset \in \Pe_f$, then $\emptyset$ is the least element of $\Pe_f$, so that 
$\rho(\emptyset)=0$ and therefore $\hat f_\emptyset =
(-1)^0=1$. Similarly, if $[n]\in \Pe_f$, then $[n]$ is the largest element in $\Pe_f$,
hence it is the last element in any maximal chain. It follows that $\rho([n])=k$ and hence
$\hat f_{[n]}=(-1)^k=1$. 
Therefore the equality \eqref{eq:dual_rank} implies that $\mathcal P_{f^*}$ differs from $\mathcal P_f$ only in the bottom  and
top elements:  $\emptyset \in \mathcal P_f$ iff  $\emptyset \notin \mathcal P_{f^*}$
and $p_n \in \mathcal P_f$ iff  $p_n \notin \mathcal P_{f^*}$. It follows that $\mathcal
P_{f^*}$ is graded as well, with rank  equal to $k-2$, $k$ or $k+2$, which in any case
is even. Furthermore, let $\rho^*$ be the rank function of $f^*$, then this also implies 
that for all $S\in \Pe_f$, $S\notin \{\emptyset, [n]\}$, we
have  $\rho^*(S)=\rho(S)\pm 1$, according to whether $\emptyset$ was added or removed. The
statement now follows from \eqref{eq:dual_rank}. 


To finish the proof, assume that the statement is true for $m<n$ and let $f\in \Fe_n^H$.
Then $f$ is either a permutation of a product of some $f_1\in \Fe_{m}^H$ and $f_2\in \Fe_{n-m}^H$, or a
dual  of such an element. By the above discussion, it follows that we only need to prove
that the statement holds for $f=f_1\otimes f_2$. But in this case, by the induction
assumption, $\Pe_{f_i}$ is graded with even rank $k_i$ and rank function $\rho_i$. We also
have
\[
f=\sum_{S\subseteq [m], T\subseteq [m-n]} (\widehat {f_1})_S(\widehat {f_2})_T p_Sp_T=
\sum_{S\subseteq [m], T\subseteq [m-n]}(-1)^{\rho_1(S)+\rho_2(T)}p_{S\cup(m+T)}.
\]
It follows that $\Pe_f=\Pe_{f_1}\times \Pe_{f_2}$ is the product of the two posets, which
is a graded poset with rank $k=k_1+k_2$ and rank function $\rho=\rho_1+\rho_2$. This
proves the statement. 




\end{proof}




\begin{example}[Chains]\label{ex:chains} Let $\Pe=\{S_1\subsetneq S_2\subsetneq \dots \subsetneq
S_N\}$ be a chain in $\mathcal L_n$. Then  $\Pe$ is graded with rank $N-1$
and rank function $\rho(S_i)=i-1$. Put 
\[
f=\sum_i (-1)^{i-1} p_{S_i}.
\]
By Proposition \ref{prop:graded}, if $f\in \Fe_n$, then the rank of $f$ must be even, so
that $N$ must be odd. 
We will show that the converse is true. We proceed by induction on $N$. For $N=1$, we have
$f=p_{S_1}\in \Fe_n^H$. Assume that the statement holds for all odd numbers $M<N$ and let
$\Pe$ be a chain as above. Then we have 
\[
f=p_{S_1}\otimes g\otimes 1_{[n]\setminus S_N}
\]
where $g$ is the function for the chain $\emptyset=S'_1\subsetneq S'_2\subsetneq \dots
\subsetneq S'_N$, with $S'_i:=S_i\setminus S_1$. This shows that we may assume that the chain
contains the least and the largest element in $\mathcal L_n$. But then 
\[
f=1+\sum_{j=2}^{N-1} (-1)^{j-1}p_{S_j}+ p_n 
\]
and
\[
f^*=1-f+p_n=\sum_{j=1}^{N-2} (-1)^{j-1}p_{T_j},
\]
where $T_j:=S_{j+1}$. By the induction assumption $f^*\in \Fe_n^H$, hence also $f=f^{**}\in \Fe_n^H$.


As we can see from Example \ref{ex:chains}, all elements in $\Fe_2^H$ are chains. This is
also true for $n=3$. Indeed, up to a permutation that does not change the chain structure, 
any $f\in \Fe_3^H$ is either a product of two elements $g\in \Fe_2^H$ and $h\in \Fe_1^H$,
or the dual of such a  product. Since $g$ must be a chain and $|\Pe_h|=1$, their product
must be a chain as well. Taking the dual of a chain only adds/removes the least/largest
elements, so the dual of a chain must be a chain as well.


\end{example}

\subsubsection{Separating type functions}



Let $\Pe\subseteq \mathcal L_n$. We say that $\Pe$ separates the points of $[n]$, or $\Pe$
is separating if for any
$i,j\in [n]$ there is some $S\in \Pe$ that contains one of the points but not the other. 
Note that in this case there can be at most one $i\in [n]$ that is not contained in any
$S\in \Pe$, so that $(\cup \Pe)^c$ is at most a singleton. Similarly, there is at most one
$i$ contained in all $S\in \Pe$, so that $\cap \Pe$ is at most a singleton. If $(\cup
\Pe)^c=\emptyset$, we say that $\Pe$ is covering.  We say that $\Pe$ is \blabla if $\cap
\Pe=\emptyset$.
We say that $f\in \Fe_n$ is
separating, covering or \blabla if $\Pe_f$ has these properties.

It is easily seen that up to a permutation, any $f\in \Fe_n$ can be written as
\[
f=p_{n_1}\otimes g\otimes 1_{[n_2]},
\]
for some $g\in \Fe_m$ which is covering and \blabla, and  that $f\in \Fe_n^H$ if and only if $g\in \Fe_m^H$. 

\begin{lemma}\label{lemma:cov_bla_sep}
Let $f\in \Fe_n$, $g\in \Fe_m$. Then
\begin{enumerate}
\item[(i)] $f\otimes g$ is covering if and only if both $f$ and $g$ are covering.
\item[(ii)] $f\otimes g$ is \blabla if and only if both $f$ and $g$ are blabla.
\item[(iii)] $f\otimes g$ is separating if and only if both $f$ and $g$ are separating,
at least one  of them is covering and at least one of them is \blabla. 
\item[(iv)] If $f$ is not covering, then $f^*$ is covering. The converse is not true.
\item[(v)] If $f$ is not \blabla, then $f^*$ is \blabla. The converse is not true.
\item[(vi)] If $f$ is separating, then $f^*$ is separating.

\end{enumerate}



\end{lemma}

\begin{proof} 
(i) and (ii) are easy to see from the equality
\[
\Pe_{f\otimes g}=\{S\cup (n+T),\ S\in \Pe_f,\ T\in \Pe_g\}\simeq \Pe_f\times \Pe_g.
\]
Indeed, since $S\subseteq [n]$ and $n+T\subseteq [n,n+m]$, we see that 
\begin{equation}\label{eq:coverbla_product}
(\cup \Pe_{f\otimes g})^c=(\cup \Pe_f)^c\cup (n+(\cup\Pe_g)^c), \quad \cap \Pe_{f\otimes g}=(\cap \Pe_f)\cup (n+\cap\Pe_g)
\end{equation}
For (iii), assume that $f\otimes g$ is separating and let $i,j\in [n]$. Then there are
some $S'\in \Pe_f$ and $T\in \Pe_g$ such that $S\cup (n+T)$ separates $i$ and $j$. But
then clearly $S$ must separate $i$ and $j$, so that $f$ is separating. Similarly, $g$ must
be separating as well. The fact that at least one of them must be covering/blabla is
immediate from \eqref{eq:coverbla_product}. 
 
 For the converse, let $i,j\in [n+m]$. If both $i,j\in [n]$, then they msut be separated
 by $\Pe_f$, hence there is some $S$ that contains one of them but not the other. Then the
 same is true for any $S\cup (n+T)$, $T\in \Pe_g$. We can similarly deal with the case
 that $i,j\in [n,n+m]$. So assume that $i\in [n]$, $j\in [n,n+m]$. By the assumption,
 there must be some $S\in \Pe_f$ and $T\in \Pe_g$, such that $i\in S$ and $j\notin (n+T)$
 (or $i\notin S$ and $j\in (n+T)$). But then $S\cup (n+T)$ separates $i$ and $j$. 

For (iv), if $f$ is not covering, then $f=(h\otimes 1_{[l]})$ for some covering $h\in
\Fe_{n-l}$. Then $\hat f_{[n]}=0$, so that $\hat f^*_{[n]}=1$. Hence $\cup\Pe_{f^*}=[n]$
and $f^*$ is covering. On the other hand, let 
$h(x)=1-\bar x_1+\bar x_1\bar x_2$ and let $f=h\otimes h\in \Fe_4^H$. It is easily checked
that both $f$ and $f^*$ are covering and \blabla.

For (v), if $f$ is not \blabla then $f=h\otimes p_l$ for some $h\in \Fe_{n-l}$, then $\hat
f_\emptyset =0$, so that $\hat f^*_\emptyset =1$, so $f^*$ is \blabla.

For (vi), let $i,j\in [n]$ and assume that $S\in \Pe_f$ is such that $i\in S$ and $j\notin
S$. Then we must have $S\in \Pe_{f^*}$, since clearly $S\neq \emptyset$ and $S\neq
[n]$. 


\end{proof}




Our next goal is to show that any type function $f\in \Fe_n^H$ of rank $k$ can be obtained 
from a separating type function  $f'\in \Fe_m^H$ such that $\Pe_f\simeq \Pe_{f'}$.


\begin{lemma}\label{lemma:separ} Let $f\in \Fe_n$ and let $f'\in \Fe_{n+1}$
be such that 
\[
f'(x_1\dots x_{n+1})=f(x_1 \dots x_{n-1}(x_n\vee x_{n+1})).
\]
Then $\Pe_f\simeq \Pe_{f'}$ and $f\in \Fe_n^H$ if and only if $f'\in \Fe_{n+1}^H$.

\end{lemma}

\begin{proof}
It can be seen using Lemma \ref{lemma:Vbasis} that for any $S\in \Pe_{f'}$, we have
\[
\hat f'_S =\begin{dcases} \hat f_S & \text{if } \{n,n+1\}\cap S=\emptyset,\\
\hat f_{S\setminus \{n+1\}} & \text{if } \{n,n+1\}\subset S,\\
0 & \text{otherwise}.
\end{dcases}       
\]
It follows that $\Pe_{f'}$ does not separate $n$ and $n+1$, moreover, from this it is
easily seen that   $\Pe_f$ is
isomorphic to $\Pe_{f'}$. 

We will show the second assertion by induction. 
Let $n=1$, so that $f'(x_1x_2)=f(x_1\vee x_2)$. If $f\in \Fe_1=\{1,1^*\}$, then either
$f'=1$ or $f'(x_1x_2)=\overline{x_1\vee x_2}=\bar x_1\bar x_2=p_2$. Conversely assume $f'\in
\Fe_2^H$. Since $f'(x_1x_2)$ has the same value for all strings different from 00, it must
be either equal to 1 or $p_2$, in which case $f$ is equal to 1 or $p_1$, repsectively. 

Assume next that the statement holds for $m<n$ and let $f\in \Fe_n^H$. Assume first that $f=(g\otimes
h)\circ \sigma$ for some $g\in \Fe_m^H$,
$h\in \Fe_{n-m}^H$ and a permutation $\sigma\in \perm_n$.  Let $\sigma(n)> m$,  
then we also have  $f'=(g\otimes h')\circ \tau$, where $h'(x_1\dots x_{m+1}) =h(x_1\dots x_{m-1}(x_m\vee x_{m+1}))$
and $\tau$ is a suitable permutaton in $\perm_{n+1}$. 
By the assumption, $h'\in \Fe_{n+1-m}^H$ so that $f'\in
\Fe_{n+1}^H$. The case $\sigma(n)\le m$ is treated similarly, replacing $h$ by $g$. 
Next, notice that since $p_{n+1}(x_1x_2\dots x_{n+1})=p_n(x_1\dots x_{n-1}(x_n\vee x_{n+1}))$,  we get
\begin{equation}\label{eq:fprime_dual}
(f')^*(x_1x_2\dots x_{n+1})=f^*(x_1\dots x_{n-1}(x_n\vee x_{n+1})),
\end{equation}
which finishes the proof in the case that $f=((g\otimes h)\circ\sigma)^*$. 


Conversely, assume that $f'\in \Fe_{n+1}^H$. By \eqref{eq:fprime_dual}, we see that it is
enough to show the statement in the case $f'=(g'\otimes h')\circ \sigma$ for some $g'\in
\Fe_m^H$, $h'\in
\Fe_{n+1-m}^H$ and a permutation $\sigma\in \perm_{n+1}$. Since
$\Pe_{f'}$ does not separate $n$ and $n+1$, any $S\in \Pe_{f'}$
either contains both  or none of them. Hence if $f'$ has the above product form,
then we must have either  both $\sigma(n),\sigma(n+1)\le m$ or both strictly
larger than $m$. Assume the latter, then (by applying a suitable permutation in
$\perm_{n+1-m}$ if
necessary) we get
\[
f(x_1\dots (x_n\vee x_{n+1}))=g'(x_{\sigma^{-1}(1)}\dots
x_{\sigma^{-1}(m)})h'(x_{\sigma^{-1}(m+1)}\dots x_{\sigma^{-1}(n-1)}x_nx_{n+1}).
\]
It follows that $f=(g'\otimes h)\circ \tau$, where $\tau\in \perm_n$ and $h\in \Fe_{n-m}^H$ is
given as
\[
h(x_1\dots x_{n-m})=h'(x_1\dots x_{n-m}x_{n-m}).
\]
By the induction assumption, $h\in \Fe_{n-m}^H$ so that $f\in \Fe_n^H$.


\end{proof}

\begin{lemma}\label{lemma:separateij}
Let $f\in \Fe_n^H$ and let $i,j\in [n]$ be such that $\Pe_f$ does not separate $i$ and
$j$. Then there is a function $f_{ij}\in \Fe_{n-1}^H$ with $\Pe_f\simeq \Pe_{f_{ij}}$, such that 
\[
f(x_1\dots x_n)=f_{ij}(x^{ij}(x_i\vee x_j)).
\]

\end{lemma}

\begin{proof} Without loss of generality we may assume that $i=n-1$, $j=n$. Put 
\[
f_{(n-1)n}(x_1\dots x_{n-1}):=f(x_1\dots x_{n-1}x_{n-1}).
\]
By the previous lemma it is enough to prove that 
\[
f(x_1x_2\dots x_n)=f_{(n-1)n}(x_1\dots (x_{n-1}\vee x_n))=f(x_1\dots x_{n-2}(x_{n-1}\vee
x_n)(x_{n-1}\vee
x_n)).
\]
Since $\Pe_f$ does not separate $n-1$ and $n$, each $S\in \Pe_f$ either contains both or
none of them. In either case,
\[
p_S(x_1x_2\dots x_n)=p_S(x_1\dots (x_{n-1}\vee x_n)(x_{n-1}\vee x_n)).
\]
This implies the statement.


\end{proof}

Clearly, the function $f_{ij}$ above is obtained from $f$ by ''glueing''  the
nonseparable indices into one index.

\begin{prop}\label{prop:separates} Let $f\in \Fe_n^H$, $r(f)=k$. Then there is a function
$g\in \Fe_{m}^H$ such that $\Pe_g$ separates the points of $[m]$, $\Pe_g\simeq \Pe_f$  and there are subsets
$I_1,\dots I_l$ of $[n]$ such that 
\[
f(x_1\dots x_n)=g(x^{\cup_j I_j}(\vee I_1)\dots (\vee I_l)).
\]


\end{prop}
\begin{proof} We can construct the function $g$ by repeated application of Lemma
\ref{lemma:separateij}, glueing together nonseparable points until, after a finite number
of steps, none are left, so that the resulting function $g$ separates the points of $m$.

\end{proof}

\begin{example}[Separating chains] Clearly, a chain $\Pe=\{S_1\subsetneq \dots \subsetneq
S_N\}$ is
separating if and only if  $S_i\setminus S_{i-1}$ is a singleton for $i=2,\dots, N$ and
both $S_1$ and $S_N^c$ are at most singletons (that is, these might be also empty). 
We have seen that the correspnding function is in $\Fe_n^H$ if and only if $N=r(\Pe)+1$ is
odd. By the separating property, we must have $n-1\le N\le n+1$, depending on whether
$S_1$ or $S_N^C$ are empty or not.
It follows that $n-2\le r(\Pe)\le n$. Since $N$ must be  odd, we see that the only
possibilities are
\begin{align*}
N&=n-1 \text{ or } N=n+1  & \text{ if $n$ is even}\\
N&=n & \text{ if $n$ is odd}.
\end{align*}

For even $n$, put
\[
\gamma_n(x):=\sum_{l=0}^n (-1)^lp_{[l]}(x)=1-\bar x_1+\bar x_1\bar x_2-\dots +\bar x_1\dots \bar x_n.
\]
Then $\gamma_n$  is a separating chain in $\Fe_n^H$ and the corresponding sets of input and output
indices  are
\[
I=\{2j, j=1,\dots n/2\},\qquad O=\{2j-1,\ j=1,\dots n/2\}.
\]

For any other separating
chain $f\in \Fe_n^H$, there is some permutation $\sigma\in \perm_n$ such that
\[
f=(p_1\otimes \gamma_{n-2}\otimes 1)\circ \sigma\ \text{ or }\  f=\gamma_n\circ \sigma.
\]
These two types are easily seen to be each others complement.
Similarly, if $n$ is odd, then any separating chain in $\Fe_n^H$  must either of the two
comlementary  forms
\[
f=(p_1\otimes \gamma_{n-1})\circ \sigma  \text{ or }\  (\gamma_{n-1}\otimes 1)\circ
\sigma
\]
for some permutation $\sigma\in \perm_n$.  From this and Example \ref{ex:chains}, we see
that up to permutations, there are  only two separating elements in $\Fe_2^H$:  
\[
f=\gamma_2,\qquad f^*=p_1\otimes 1_1,
\]
that are complementary. Similarly, there are basically 
two complementary forms of  separating elements in $\Fe_3^H$: 
\[
f=p_1\otimes \gamma_2,\qquad f^*= \gamma_2\otimes 1. 
\]


\end{example}

The following properties of $\gamma_n$ are easily checked directly.

\begin{lemma}\label{lemma:gamma} Let $n\in \mathbb N$ be even.
\begin{enumerate}
\item[(i)] $(\gamma_n\otimes 1_1)^*=p_1\otimes \gamma_n$,
\item[(ii)] $(p_1\otimes\gamma_n \otimes 1)^*=\gamma_{n+2}$.
\end{enumerate}


\end{lemma}

\begin{example}[$\Fe_4^H$]\label{ex:type4} We will describe all separating elements
$f\in \Fe_4^H$, up to permutations. We have  $f=g\otimes h$ or $f=(f\otimes g)^*$  for some $g\in
\Fe_m^H$, $h\in \Fe_l^H$. Then either $m=1$, $l=3$ or $m=l=2$. In the first case, $h$ is a
chain in $\Fe_3^H$. In order for $f$ to be separating, $h$ must be separating and if
$g=1_1$, then $h$ must be covering, if $g=p_1$, then $h$ must be \blabla. Together with
complements, this gives the functions:
\[
f=1_1\otimes \gamma_2\otimes p_1,\qquad f=\gamma_4.
\]
In the other case, $g$ and $h$ must be separating elements in $\Fe_2^H$. The only new
functions obtained in this way are
\begin{align*}
f&= \gamma_2\otimes \gamma_2=1-\bar x_1-\bar x_3+\bar x_1\bar x_2+\bar x_1\bar x_3+\bar x_3\bar x_4- \bar x_1\bar
x_2\bar x_3-\bar x_1\bar x_3\bar x_4+\bar x_1\bar x_2\bar x_3\bar x_4\\
f^*&=  (\gamma_2\otimes \gamma_2)^*=\bar x_1+\bar x_3-\bar x_1\bar x_2-\bar x_1\bar x_3-\bar x_3\bar x_4+ \bar x_1\bar
x_2\bar x_3+\bar x_1\bar x_3\bar x_4
\end{align*}



\end{example}

Let us now introduce the labeling of all separating chains as follows:
\[
\gamma_{i,n}=\begin{dcases} \gamma_n & \text{if $i=0$, $n$ is even}\\
\gamma_n^*=p_1\otimes \gamma_n\otimes 1_1 & \text{if $i=1$, $n$ is even}\\
\gamma_{n-1}\otimes 1_1 & \text{if $i=0$, $n$ is odd}\\
p_1\otimes \gamma_{n-1} & \text{if $i=1$, $n$ is odd}.
\end{dcases}
\]


\begin{lemma}\label{lemma:product_le} For $i,j\in \{0,1\}$, $n,m\in \mathbb N$,  we have 
\[
\gamma_{i,n}\otimes \gamma_{j,m}=?
\]

\end{lemma}






\subsubsection{Paths}

Let $f\in \Fe_n^H$, assume that $f$ separates points of $[n]$. 
We will study the structure of $\Pe_f$ in more detail.

For each $i\in [n]$, let $\Pe_{f,i}:=\{S\in \Pe_f,\ i\in S\}$ and let $\mathcal M_{f,i}$ be the
set of minimal elements in $\Pe_{f,i}$. Elements of $i$ will be called minimal sets for
$i$. Note that $\Pe_{f,i}$ can be empty, there is a unique index with this property, it
will be called the free output. 
Another case is when $\Pe_{i,f}=\mathcal M_{f,i}=\{[n]\}$, there is again a unique index with this
property, it will be called the first input of $f$. Note that taking complements turns the
first input into the free output and vice versa.


\begin{lemma}\label{lemma:points} 
\begin{enumerate}
\item[(i)]  All minimal sets of $i$ have the same rank $r_f(i)$, called the rank of $i$. If
$\mathcal M_{f,i}=\emptyset$, we put $r_f(i)=r(f)+1$. 
\item[(ii)] $i\in O_f$ if and only if $r_f(i)$ is odd.

\end{enumerate}


\end{lemma}

\begin{proof}  We will proceed by induction. Both  assertions are quite trivial for $n=1$,
assume the statements hold for $m<n$ and let $f\in \Fe_n^H$. Assume first that the assertions are
true for $f$, then it is easily observed that they hold also for any permutation $f\circ
\sigma$.
Next, note that $\Pe_{f^*}$ differs from $\Pe_f$ only up to adding/removing the least and greatest elements $\emptyset$ and
$p_n$. Let $\Me_{f^*,i}=\{[n]\}$, then (i) is trivially satisfied and
$r_{f^*}(i)=\rho_{f^*}([n])=k=r(f^*)$ is even. Since $i\ne S$ for any $S\in \Pe_{f^*}$
other than $[n]$, we have
\[
f^*(e^i)=\sum_{S\in \Pe_{f^*}, S\ne [n]} \hat f^*_S=1-p_n=0,
\]
so that $i\in I_{f^*}$ and (ii) holds. If $\Me_{f^*,i}=\emptyset$, then by definition
$r_{f^*}(i)=r(f^*)+1$ is odd and clearly $f^*(e^i)=f^*(0)=1$, so that $i\in O_{f^*}$. 
Assume now that $\Me_{f^*,i}$ is nonempty and not equal to $\{[n]\}$. Then the same is
true for $\Me_{f,i}$, and by the assumption, $\rho_{f}(S)=r_f(i)$ for all elements  $S\in
\Me_{f,i}$. Then $\rho_{f^*}(S)=\rho_f(S)\pm 1$, depending only on the fact whether $\emptyset
\in \Pe_f$. It follows that $\rho_{f^*}(S)$ has the same value for all minimal sets for
$i$, and this value is odd if and only if $r_f(i)$ is even. Since complementation
exchanges inputs and outputs, the statements are proved for $f^*$.

Let now $f\in \Fe_n^H$ be arbitrary and let $i\in [n]$. As we have seen, the statement
holds if $i$ is the free output or the first input, so assume that $\emptyset\ne
\Me_{f,i}\ne \{[n]\}$. By the first part of the proof, it is enough to assume that
$f=g\otimes h$ for some $g\in \Fe_m^H$ and $h\in \Fe_{n-m}^H$. 
Suppose without loss of generality that $i\in [m]$, then clearly $\Me_{g,i}\ne \emptyset$
and $\Me_{f,i}$ consists of $S\cup T$, with $S\in \Me_{g,i}$ and $T$ a minimal element in
$\Pe_h$. Since $\rho_h(T)=0$ for any minimal element $T$, we have
\[
\rho_f(S\cup T)=\rho_g(S)+\rho_h(T)=r_g(i),\qquad \forall S\cup T \in \Me_{f,i}.
\]
The statement (ii) follows from the fact that $i\in O_f$ if and only if $i\in O_g$. 




\end{proof}



\end{document}

We present some important categories.

\subsection{The category $\FV$}

Let  $\FV$ be the category of finite dimensional real vector spaces with linear maps. Then
$(\FV,\otimes, \mathbb R)$ is a symmetric monoidal category, with the usual tensor product
of vector spaces. With the usual duality $(-)^*: V\mapsto V^*$  of vector spaces, $\FV$ is
compact closed.  We will always use the identification $V=V^{**}$ by the canonical
isomorphism.

Put
\[
e_U: U\otimes U^*\to \mathbb R,\qquad e_U(u\otimes u^*)=\<u^*,u\>,
\]
then $e_U$ is the cap (counit) for the duality of $U$ and $U^*$. The unit (cup) of the
duality is 
\[
\eta_U: \mathbb R\to U^*\otimes U, \qquad \eta_U(1)=\sum_i e_i^*\otimes e_i,
\]
where $\{e_i\}$ is a basis of $U$ and $\{e_i^*\}$ the dual basis of $U^*$, determined by
$\<e_i^*,e_j\>=\delta_{ij}$. It is easily verified that $\eta_U$ does not depend on the
choice of the basis $\{e_i\}$. We will identify $\eta_U:=\eta_U(1)$. Note that $\eta_U$ is
just $e_U$ seen as an element in $(U\otimes U^*)^*=U^*\otimes U$.

By compactness, the internal hom is  $[U,V]=U^*\otimes V$. Note that we have the usual identification 
\begin{equation}\label{eq:fvhoms}
\<f(u),v^*\>=\<w,u\otimes v^*\>,\qquad u\in U,\
v^*\in V^*
\end{equation}
between maps $f:U\to V$ and elements $w\in U^*\otimes V=[U,V]$, so the internal hom is
identified with  the set of all morphisms $U\to V$.  The above relation of $f$ and $w$ can be also
written as
\[
f(u)=(e_U\otimes V)(u\otimes w),\qquad 
w=(f^*\otimes V)(\eta_V),
\]
(we write $V$ for the identity map  $id_V$). Here $f^*$ is the usual adjoint map
$f^*:V^*\to U^*$.  

The composition $\circ$ defines a map
\[
[U,V]\otimes [V,W]\to [U,W],
\]
using the identification $[U,V]=U^*\otimes V$, $\circ$ is identified with 
\[
U^*\otimes V\otimes V^*\otimes W\xrightarrow{U^*\otimes e_V\otimes W} U^*\otimes W.
\]
Using symmetry and $e_V$, we can also define partial compositions through $V$ in an obvious way.
This can be depicted graphically in a nice way.


\subsection{Affine subspaces}

A subset $A\subseteq V$ of a finite dimensional vector space $V$ is an affine subspace if 
$\sum_i\alpha_i a_i\in A$ whenever all $a_i\in A$ and $\sum_i\alpha_i=1$. We say that $A$
is proper if $0\ne A$ and $A\ne \emptyset$. We will always
mean  that an affine subspace is proper (if not explicitly stated otherwise).

\subsubsection{Description}
An affine
subspace can be determined in two ways:
\begin{enumerate}
\item[(i)] Let $L\subseteq V$ be a linear subspace and $a_0\ne L$. Then 
\[
A=a_0+L
\]
is a proper affine subspace.  Note that $a_0\in A$ and $A\cap L=\emptyset$.
Conversely, any proper affine subspace $A$ can be given in this way, with $a_0$ an arbitrary element in $A$ and
\[
L=\lin(A):=\{a_1-a_2,\ a_1,a_2\in A\}=\{a-a_0,\ a\in A\}.
\]
\item[(ii)] Let $S\subseteq V$ be a linear subspace and $a_0^*\in V^*\setminus S^\perp$. Then
\[
A=\{a\in S, \<a_0^*,a\>=1\}
\]
is a proper affine subspace. Conversely, any proper affine subspace $A$ is given in this way, with
$S=\Span(A)$ and $a_0^*$ an arbitrary element in the dual 
\[
\tilde A=\{a^*\in V^*,\ \<a^*,a\>=1,\ \forall a\in A\}.
\]
\end{enumerate}

For an affine subspace $A$, the relation of $L=\lin(A)$ and $S=\Span(A)$ is as follows:
\[
S=L+\mathbb R a,\qquad L=S\cap \{\tilde a\}^\perp,
\]
here $a\in A$ and $\tilde a\in \tilde A$ are arbitrary elements.


\subsubsection{Duality}

For an affine subspace $A$,  $\tilde A$ is an affine subspace as well. If $A$ is proper,
then $\tilde A$ is proper and we have
$\tilde{\tilde A}=A$. More generally, if $\emptyset\ne C\subseteq A$ is any  subset of a
proper  affine
subspace $A$, then $\tilde C$ is a proper affine subspace 
and $\tilde{\tilde C}$ is the affine hull of $C$, that is,
\[
\tilde{\tilde C}=\aff(C):=\{\sum_i \alpha_i c_i,\ c_i\in C,\ \sum_i\alpha_i=1\}.
\]
In this case, we may write $\tilde{\tilde C}$ as
\[
\tilde{\tilde C}=c_0+\lin(C)=c_0+\Span(\{c_1-c_2,\ c_1,c_2\in C\})
\]
with an arbitrary element $c_0\in C$, or as
\[
\tilde{\tilde C}=\{c\in \Span(C),\ \<a_0^*,c\>=1\}
\]
for an arbitrary element $a_0^*\in \tilde A$.

\begin{lemma}\label{lemma:duality}
Let $A$ be a proper affine subspace and let $C\subseteq A$ be any subset. Then
\begin{align*}
\lin(C)&=\lin(\tilde{\tilde C})=\tilde
C^\perp=\Span(\tilde C)^\perp,&  \lin(\tilde C)&=C^\perp=\Span(C)^\perp \\
\Span(C)&=C^{\perp\perp} =\lin(\tilde C)^\perp,&  \Span(\tilde C)&=\lin(C)^\perp.
\end{align*}


\end{lemma}


\subsubsection{The lattice of affine subspaces}

Let $\Ae(V)$ be the set of all affine subspaces in a finite dimensional vector space $V$.
Then $\Ae(V)$ can be ordered by inclusion and it is a complete lattice, with
\[
\wedge \Ae=\cap \Ae,\qquad \vee \Ae = \{\sum_i\alpha_i a_i,\ a_i\in A_i\in \Ae,
\sum_i\alpha_i=1\}
\]
for any subset $\Ae\subseteq \Ae(V)$. Let us choose any nonzero elements $a\in V$,
$\tilde a\in V^*$ and put
\[
\Ae_{a,\tilde a}(V)=\{A\in \Ae(V),\ a\in A,\ \tilde a\in \tilde A\}.
\]
Note that any subspace in $\Ae_{a,\tilde a}$ is proper and it is a complete sublattice in
$\Ae(V)$. Moreover, we have
\[
\lin(\wedge\Ae)=\wedge\{\lin(A),\ A\in \Ae\},\qquad \lin(\vee\Ae)=\vee\{\lin(A),\ A\in \Ae\}
\]
and similarly for $\Span$. 

We say that $A,B\in \Ae_{a,\tilde a}(V)$ are independent if $A\cap B=\{a\}$, equivalently,
$\lin(A)\cap\lin(B)=\{0\}$, that is, $\lin(A)$ and $\lin(B)$ are independent linear
subspaces. A family $\{A_1,\dots,A_n\}\subseteq \Ae_{a,\tilde a}(V)$ is independent if
$A_i$ and $\vee_{j\in I}A_j$ are independent for any $i\in \{1,\dots,n\}$ and $i\ne
I\subseteq\{1,\dots,n\}$. Equivalently, $\{\lin(A_1),\dots,\lin(A_n)\}$ is an independent
family of subspaces in $V$. 

\begin{lemma}\label{lemma:affine_distributive} Let $\{A_1,\dots,A_n\}\subseteq
\Ae_{a,\tilde a}(V)$ be an independent family. Then the sublattice generated by
$\{A_1,\dots,A_n\}$ is distributive.



\end{lemma}

\begin{proof} Clear from a similar property of linear subspaces.   

\end{proof}


\subsection{The category $\Af$}


The objects of $\Af$ are of the form $X=(V_X,A_X)$, where $V_X$ is an object in 
$\FV$ and  $A_X\subseteq V_X$ a proper affine subspace. Morphisms $X\to Y$ are morphisms
$f:V_X\to V_Y$ in $\FV$ such that
$f(A_X)\subseteq A_Y$.  We may
also add
two special objects: the initial object $\emptyset:=(\{0\}, \emptyset)$ and the terminal
object $0:=(\{0\},\{0\})$, here the affine subspaces are obviously not proper.


For any object $X$, we also put 
\[
L_X:=\lin(A_X)\qquad S_X:=\Span(A_X),\qquad  d_X:=\dim(L_X),\qquad D_X:=\dim(V_X).
\]
Note that $X$ is
uniquely determined also by the triple $(V_X,L_X,a_X)$ with  an element $a_X\in A_X$, or
by $(V_X,S_X,\tilde a_X)$ with an element $\tilde a_X\in \tilde A_X$. 




\subsubsection{Limits and colimits}

Limits and colimits should be obtained from those in $\FV$, we have to spectify the other
structures and check  whether the corresponding arrows are in $\Af$. 

\medskip

First, note that $\{0\}$ is both initial and terminal in $\FV$. In $\Af$, it is easily
seen that $\emptyset$ is {initial} and $0$ is {terminal} in $\Af$. 

Let $\bX$, $\bY$ be two objects in $\Af$. Assume first that both are proper. We define
their {product} as
\[
\bX\times \bY:=(V_\bX\times V_\bY, A_\bX\times A_\bY, (a_X,a_Y), \frac12(\tilde a_X,\tilde
a_Y)),
\]
where 
\[
A_\bX\times A_\bY:=\{(x,y)\in V_\bX\times V_\bY,\ x\in A_\bX, y\in A_\bY\}
\]
is the direct product of $A_\bX$ and $A_\bY$. It is easily verified that this is indeed an
affine subspace and the usual projections $\pi_\bX:V_\bX\times V_\bY\to V_\bX$ and $\pi_\bY:V_\bX\times
V_\bY\to V_\bY$ are in $\Af$. Moreover, for $f:\bZ\to \bX$  and $g:\bZ\to \bY$, the map
$f\times g(z)=(f(z),g(z))$ is also clearly a morphism $\bZ\to \bX\times\bY$  in $\Af$. 
We have
\[
L_{X\times Y}=L_X\times L_Y,\qquad S_{X\times Y}= (L_X\times L_Y)\vee \mathbb R(a_X,a_Y)=(S_X\times S_Y)\wedge \{(\tilde
a_X,-\tilde a_Y)\}^\perp
\]
for an arbitrary choice $a_X\in A_X$, $a_Y\in A_Y$ and $\tilde a_X\in \tilde A_X$, $\tilde
a_Y\in \tilde A_Y$.

Next, we put $X\times \emptyset=\emptyset$, with the unique morphisms $\pi_X:\emptyset \to X$
and $\pi_{\emptyset}:\emptyset \to \emptyset$. If $Y\xrightarrow{f}X$ and
$Y\xrightarrow{g} \emptyset$, then it is clear that $Y=\emptyset$, this shows that this is
indeed the product. Further, put  $X\times 0=X$, with $\pi_X=id_X$  and
$\pi_0: X\xrightarrow{!}0$. It is also readily verified that this is the product.

\medskip

The coproduct for proper objects $X$, $Y$ is defined as 
\[
\bX\oplus \bY=(V_\bX\times V_\bY, A_\bX\oplus A_\bY)
\]
where 
\[
A_\bX\oplus A_\bY:=\{(tx,(1-t)y),\ x\in A_{\bX}, y\in A_\bY,\ t\in \mathbb R\}
\]
is the direct sum. To check that this is an affine subspace, let $x_i\in A_\bX$, $y_i\in A_\bY$, $s_i\in
\mathbb R$ and let $\sum_i\alpha_i=1$, then 
\[
\sum_i\alpha_i(s_ix_i,(1-s_i)y_i)=(\sum_is_i\alpha_ix_i,\sum_i(1-s_i)\alpha_iy_i)=(sx,(1-s)y)\in
A_\bX\oplus A_\bY,
\]
where $s=\sum_is_i\alpha_i$, $x=s^{-1}\sum_is_i\alpha_ix_i$ if $s\ne 0$ and is arbitrary
in $A_\bX$ otherwise, similarly $y=(1-s)^{-1}\sum_i(1-s_i)\alpha_iy_i$ if $s\ne 1$ and is
arbitrary otherwise. The usual embeddings  $p_\bX:V_\bX\to V_\bX\times V_\bY$ and $p_\bY:
V_{\bY}\to V_\bX\times V_\bY$ are easily seen to be morphsims in $\Af$.   

Let  $f:\bX\to \bZ$, $g:\bY\to \bZ$ be any morphisms in $\Af$ and consider the map
$V_\bX\times V_\bY\to V_\bZ$ given as
$f\oplus g(u,v)=f(u)+g(v)$. We need to show that it preserves the affine subspaces. So let 
$x\in A_\bX$, $y\in  A_\bY$, then since $f(x),g(y)\in A_\bZ$, we have for any $s\in \mathbb R$,
\[
f\oplus g(sx,(1-s)y)=sf(x)+(1-s)g(y)\in A_\bZ.
\]
We also have
\[
L_{X\oplus Y}= (L_X\times L_Y)\vee \mathbb R\{(a_X,-a_Y)\},\qquad S_{X\oplus Y}=S_X\times
S_Y
\]
for some $a_X\in A_X$, $a_Y\in A_Y$.

Similarly as in the case of products, it is verified that $X\oplus \emptyset=X$ and
$X\oplus 0=0$. (All the statements for coproducts can be obtained from duality defined
below).

\medskip

One can also discuss equalizers and coequalizers, here we only note that these may be
trivial even for proper objects. We will  consider pullbacks and pushouts for some special
morphisms that will be needed below.

\subsubsection{Mono-, epi- and bimorphisms} 


A morphism $X\xrightarrow{f} Y$ is a monomorphism if $f\circ h=f\circ g$ implies $h=g$ for
any morphisms $g$, $h$, and an epimorphism if $h\circ f=g\circ f$ implies $h=g$. A
morphism that is both mono and epi is called a bimorphism.


\begin{lemma}\label{lemma:epimono} A morphism $X\xrightarrow{f} Y$ is a  monomorphism if and only
if  it is injective as a map $f:V_X\to V_Y$. Similarly, $f$ is an epimorphism if and only if it is surjective. 

\end{lemma}

Consequently, $f$ is a bimorphism if and only if  it is an isomorphism of $V_X$ and $V_Y$. Note that a
bimorphism is not necessarily an isomorphism in $\Af$.

\begin{proof} Since injective maps are monomorphisms in $FV$, it is clear that any such
map is a monomorphism also in $\Af$. For the converse, let $F$ be a monomorphism in $\Af$
and let $K=Ker(f)$. Let $Z=(V_X\times K, A_X\times \{0\})$, then $Z$ is an object in
$\Af$. Let $g,h:V_Z\to V_X$ be defined as $g=\pi_{V_X}$, $h=\pi_{V_X}+\pi_K$, then
$g,h:Z\to X$ are morphisms in $\Af$ and we have
\[
f\circ g(x,y)=f(x)=f(x)+f(y)=f\circ h(x,y),\qquad \forall (x,y)\in V_Z.
\]
Hence $h=g$, so that we must have $K=\{0\}$. 

Similarly, let $f$ be an epimorphism and let $R=f(V_X)\subseteq V_Y$. Let $Z=(V_Y\times
V_Y|_R,
A_Y\times \{[0]\})$ and let $g,h:V_Y\to V_Z$ be given by $g(y)= (y,[0])$, $h(y)=(y, q(y))$,
where $q:V_Y\to V_Y|_R$ is the quotient map. Since $A_Y\subseteq R$, we have
$q(A_Y)=\{[0]\}$, so that both $g,h$ are morphisms in $\Af$. Moreover,
\[
g\circ f(x)=(f(x),[0])=(f(x),q(f(x)))= h\circ f,
\]
so that $g=h$, but this implies that $R=V_Y$.


\end{proof}

\subsubsection{Pullbacks and pushouts}

Let $X,Y, Z$ be proper objects such that there are bimorphisms 
\[
Z\xrightarrow{f} X,\qquad Z\xrightarrow{g} Y.
\]
Note that in particular $\psi:=f\circ g^{-1}$ is an isomorphism of $V_Y$ onto $V_X$. 
%Let us also assume that there is some $\tilde a_x\in \tilde A_X$ such that $\psi^*(\tilde
%a_X)\in \tilde A_Y$. 

Let us define  $X\sqcup_{f,g} Y:=(V_X,A_{X\sqcup_{f,g} Y})$, with 
\[
A_{X\sqcup_{f,g} Y}=\{sa+(1-s)\psi(b),\ a\in A_X,\ b\in A_Y,\ s\in \mathbb R\}.
\]
Note first that this is a proper object in $\Af$ if and only if 
\begin{equation}\label{eq:pushout_cond}
\forall b\in A_Y,\quad t\psi(b)\in A_X \ \implies \ t=1.
\end{equation}
Indeed, we only have to check that
$0\notin A_{X\sqcup_{f,g}Y}$ which is easily seen to be equivalent to
\eqref{eq:pushout_cond}. 

Assume \eqref{eq:pushout_cond}, then $X\sqcup_{f,g} Y$ together with the morphisms given by the linear maps
$id:V_X\to V_X$ and $\psi:V_Y\to V_X$,  is the \textbf{pushout} of the above diagram. Indeed, these are clearly bimorphisms $X\to X\sqcup_{f,g} Y$ and $Y\to X\sqcup_{f,g} Y$ in $\Af$, and we have 
\[
id\circ f=f=\psi\circ g.
\]
Also, if  $W$ is an object in $\Af$ and $X\xrightarrow{i} W$ and $Y\xrightarrow{j} W$ are such that $i\circ f=j\circ
g$, then $i=i\circ id$, $j=i\circ \psi$, so the map $i$ defines a morphism
$X\sqcup_{f_0,g_0} Y\to W$,
obviously unique, with the required properties. We have
\[
L_{X\sqcup_{f,g}Y}=L_X\vee \psi(L_Y),\qquad S_{X\sqcup_{f,g}Y}=S_X\vee
\psi(S_Y).
\]
Let us also note that if \eqref{eq:pushout_cond} is not satisfied,  there is some $z\in V_Z$ such
that for some $t\ne 1$,
\[
tf(z)\in A_X,\qquad g(z)\in A_Y.
\]
If there are some $X\xrightarrow{i} W$ and $Y\xrightarrow{j} W$ as above, then 
$ti\circ f(z)\in A_W$, but also $i\circ f(z)=j\circ g(z)\in A_W$, so that $W$ is not a
proper object, in this case the pushout is the terminal object $0$, with the unique arrows
$X\xrightarrow{!} 0$, $Y\xrightarrow{!} 0$.

Similarly, let 
\[
X\xrightarrow{f} Z,\qquad Y\xrightarrow{g} Z
\]
be  bimorphisms and let $\psi=f^{-1}\circ g$. If 
\begin{equation}\label{eq:pullback_cond}
\phi(A_Y)\cap A_X\ne \emptyset,
\end{equation}
 the \textbf{pullback} of $f, g$ is
$X\sqcap_{f,g}Y=(V_X, A_X\cap \phi(A_Y))$, 
with  the bimorphisms given by $id_X$ and $\phi^{-1}$. In this case
\[
L_{X\sqcap_{f,g}Y}=L_X\cap \phi(L_Y),\qquad S_{X\sqcap_{f,g}Y}=S_X\cap \phi(S_Y).
\]
Without  condition \eqref{eq:pullback_cond}, the above is not a proper object and in 
this case the pulback is the initial object $\emptyset$.

%\subsubsection{Bimorphism ordering and lattices of objects}
%
%Let $\Fe=\{X_\alpha\}_{\alpha\in \mathcal A}$ be a family of objects in $\Af$ such that there
%are objects $X_{in}$, $X_{out}$ and bimorphisms
%\[
%X_{in}\xrightarrow{u_\alpha} X_\alpha \xrightarrow{v_\alpha} X_{out},
%\]
%$V_{X_{in}}=V_{X_{out}}$ and $v_\alpha\circ u_\alpha=id$ for $\alpha\in \mathcal A$.
%Moreover, there are some elements $\tilde x_{in}\in \tilde A_{X_{in}}$, $x_{out}\in
%A_{X_{out}}$ and $x_\alpha\in A_{X_\alpha}$, $\tilde x_\alpha\in \tilde A_{X_\alpha}$ such
%that $u_\alpha^*(\tilde x_\alpha)=\tilde x_{in}$ and $v_\alpha(x_\alpha)=x_{out}$ for all
%$\alpha\in \mathcal A$. We have:
%
%\begin{enumerate}
%\item Let $X_\alpha \le X_\beta$ if there is a bimorphism $X_\alpha\xrightarrow{f}
%X_\beta$ such that $v_\beta\circ f=v_\alpha$ and $f\circ u_\alpha=u_\beta$. Then
%$\le$ is up to isomorphisms a partial order in $\Fe$. Indeed, $\le$ is obviously a preorder. Assume
%$X_\alpha\le X_\beta$ with the bimorphism $f$ and   $X_\beta\le X_\alpha$ with the
%bimorphism $g$. Then 
%\[
%f\circ g=f\circ u_\alpha\circ v_\alpha\circ g=u_\beta\circ v_\beta=id,
%\]
%so that $X_\alpha$ and $X_\beta$ are isomorphic. 
%
%
%
%\end{enumerate}
%
%
%
%




%Let us turn to equalizers. So let $f,g:\bX\to \bY$ and let 
%\[
%V_E=\{v\in V_\bX,\ f(v)=g(v)\}. 
%\]
%Let $h: \bZ\to \bX$ equalize $f,g$, then $h(V_\bZ)\subseteq V_E$ and $h(A_\bZ)\subseteq
%A_\bX\cap V_E$, so that $A_\bX\cap V_E$ must be nonempty. In this case, 
%\[
%\bE=(V_E, A_E:=V_E\cap A_\bX, a_E,\tilde a_E:=\tilde a_X)
%\]
%with the inclusion map $V_E\hookrightarrow V_\bX$ is an
%equalizer of $f,g$ for any choice of $a_E\in A_E$ (note that choosing another $a_E$ gives
%us an isomorphic object in $\Af$). If the
%intersection $V_E\cap A_\bX$ is empty, then the only equalizing arrow 
%for $f$ and $g$ is $\emptyset\to \bX$, which is
%then the equalizer.
%
%For the coequalizer, let $V_Q$ be the quotient space $V_Q:=V_\bY|_{Im(f-g)}$ and let
%$q:V_\bY\to V_Q$
%be the quotient map. If  some $h: \bY\to \bZ$ coequalizes $f$ and $g$, then $h$ maps
%$Im(f-g)$ to 0, so that $Im(f-g)\cap A_\bY=\emptyset$, unless $\bZ$ is the terminal
%object. It is easily checked that if $Im(f-g)\cap A_\bY=\emptyset$, then
%\[
%Q=(V_Q,A_Q:=q(A_\bY),a_Q:=q(a_Y),\tilde a_Q )
%\]
%together with the quotient map  $q$ is the
%coequalizer of $f$ and $g$ for any choice of $\tilde a_Q\in \tilde A_Q$.
%If the intersection is nonempty,
%then the unique coeqalizing arrow is $\bY\to 0$, which is then the coequalizer.
%
%Let us mention pullbacks and pushouts. Since pullbacks can be obtained from products and
%equalizers, we see that we have a similar situation: if a pullback is ''well defined'',
%then it coincides with the pullback in $\FV$, otherwise it is trivial. More precisely, if 
%$f:\bX\to \bZ$ and $g:\bY\to \bZ$, then we put 
%\[
%V_P:=\{(x,y)\in V_\bX\times V_\bY, f(x)=g(y)\}.
%\]
%If $V_P\cap A_\bX\times A_\bY\ne \emptyset$, that is, there are some $x\in A_\bX$ and $y\in
%A_\bY$ such that $f(x)=g(y)$, then 
%\[
%(V_P,A_P:=(A_\bX\times A_\bY)\cap V_P, a_P, \frac 12(\tilde a_X,\tilde a_Y))
%\]
%with the two projections
%is a pullback of $f$ and $g$ for any choice of $a_P\in A_P$, otherwise the pullback is
%just the initial object $\emptyset$.
%
%Similarly, let $f:\bZ\to \bX$, $g:\bZ\to \bY$, then let $V_Q$ be the quotient of
%$V_\bX\times V_\bY$ by the subspace
%\[
%\{(f(z),-g(z)),\ x\in V_\bZ\}.
%\]
%If this subspace does not contain any element of $A_\bX\oplus A_\bY$, that is, there is no
%$z\in V_\bZ$ such that for some $t\in \mathbb R$,
%\[
%f(tz)\in A_\bX,\qquad g((t-1)z)\in A_\bY,
%\]
%then 
%\[
%Q=(V_Q, A_Q:=q(A_\bX\oplus A_\bY), \frac12 q(a_X,a_Y), \tilde a_Q)
%\]
%with maps $x\mapsto q(x,0)$ and $y\mapsto q(0,y)$ is the
%pushout of $f$ and $g$. Otherwise the pushout is just $0$.
%
\subsubsection{Monoidal structure}

Let $X$, $Y$ be objects in $\Af$. Let us define
\[
A_{X\otimes Y}:=\{x\otimes y, x\in A_X, y\in A_Y\}^{\approx}.
\]
In other words, $A_{X\otimes Y}$ is the smallest affine subspace in $V_X\otimes V_Y$ containing
$A_X\otimes A_Y$. 

\begin{lemma}\label{lemma:tensor_spaces}
For any $a_X\in A_X$, $a_Y\in A_Y$, we  have
\begin{align}
L_{X\otimes Y}&=\lin(A_X\otimes A_Y)=\Span(\{x\otimes y-a_X\otimes a_Y,\ x\in A_X,\ y\in
A_Y\})\notag\\
&= (a_X\otimes L_Y)+ (L_X\otimes a_Y)+ (L_X\otimes L_Y)\label{eq:lxy}\\
&= S_X\otimes L_Y+L_X\otimes a_Y=a_X\otimes L_Y+L_X\otimes S_Y
\end{align}
(here $+$ denotes the direct sum of subspaces). We also have
\[
S_{X\otimes Y}=S_X\otimes S_Y.
\]
\end{lemma}

\begin{proof} Let $x\in A_X$, $y\in A_Y$, then
\[
x\otimes y-a_X\otimes a_Y=a_X\otimes (y-a_Y)+(x-a_X)\otimes a_Y+(x-a_X)\otimes (y-a_Y),
\]
so that $L_{X\otimes Y}=\lin(A_X\otimes A_Y)$ is contained in the subspace on the RHS of \eqref{eq:lxy}.
Let $d$ be the dimension of this subspace, then clearly
\[
d_{X\otimes Y}\le d\le d_X+d_Y+d_Xd_Y.
\]
On the other hand, any element of $S_X$ has the form $tx$ for some $t\in \mathbb R$ and
$x\in A_X$, so that it is easily seen that $S_X\otimes S_Y=S_{X\otimes Y}$. 
Hence 
\begin{align*}
d_{X\otimes Y}&=\dim(L_{X\otimes Y})=\dim(S_{X\otimes
Y})-1=\dim(S_X)\dim(S_Y)-1=(d_X+1)(d_Y+1)-1\\
&=d_X+d_Y+d_Xd_Y.
\end{align*}
This completes the proof.

\end{proof}



For $X,Y$ in $\Af$, put $X\otimes Y:=(V_X\otimes V_Y,A_{X\otimes Y})$.
Note that by this definition, $X\otimes \emptyset =\emptyset$ and
$X\otimes 0=0$ unless $X=\emptyset$, in which case $\emptyset\otimes 0=\emptyset$. 
Also let $I:=(\mathbb R, \{1\})$. 


\begin{lemma}\label{lemma:monoidal}
$(\Af,\otimes, I)$ is a symmetric
monoidal category.
\end{lemma}

\begin{proof} Note that this structure is inherited from the symmetric monoidal structure
in $\FV$. To show that $\otimes$ is a functor, we have to check that for $X_1\xrightarrow{f} Y_1$ and $X_2\xrightarrow{g} Y_2$ in
$\Af$, we have $X_1\otimes Y_1\xrightarrow{f\otimes g} X_2\otimes Y_2$ which amounts to
showing that 
\[
(f\otimes g)(A_{X_1\otimes Y_1})\subseteq A_{X_2\otimes Y_2}.
\]
Let $x\in A_{X_1}$, $y\in A_{Y_1}$, then $f(x)\otimes g(y)\in A_{X_2}\otimes
A_{Y_2}\subseteq A_{X_2\otimes Y_2}$. Since  $A_{X_1\otimes Y_1}$ is the affine subspace
generated by $A(X_1)\otimes A(Y_1)$, the above inclusion follows by linearity of $f\otimes
g$. 

It only remains to prove that the associators, unitors and symmetries from
$\FV$ are morphisms in $\Af$. Indeed, let $\alpha_{X,Y,Z}:V_X\otimes (V_Y\otimes V_Z)\to
(V_X\otimes V_Y)\otimes V_Z$ be the associator in $\FV$. We need to check that
$\alpha_{X,Y,Z}(A_{X\otimes(Y\otimes Z)})\subseteq A_{(X\otimes Y)\otimes Z}$. It is easily
checked that $A_{X\otimes(Y\otimes Z)}$ is the affine span of elements of the form
$x\otimes (y\otimes z)$, $z\in A_X$, $y\in A_Y$ and $z\in A_Z$, and we have
\[
\alpha_{X,Y,Z}(x\otimes (y\otimes z))=(x\otimes y)\otimes z\in A_{(X\otimes Y)\otimes Z}
\]
for all such elements. The desired inclusion follows by linearity.
The proof of the other inclusions is similar.

\end{proof}



\subsubsection{Duality}

We define $X^*:=(V_X^*,\tilde A_X)$. Note that we have
\[
L_{X^*}=S_X^\perp,\qquad S_{X^*}=L_X^\perp,\qquad d_{X^*}=D_X-d_X-1.
\]
It is easily seen  that $(-)^*$ defines a full and faithful functor $\Af^{op}\to \Af$,
moreover, $X^{**}=X$ (we will use  the canonical identification of  any $V$ in $\FV$ with its second dual). 


\begin{theorem} $(\Af,\otimes,I)$ is a *-autonomous category, with duality $(-)^*$, such
that $I^*=I$.

\end{theorem}


\begin{proof} We only need to check the natural isomorphisms 
\[
\Af(X\otimes Y,Z^*)\simeq \Af(X,(Y\otimes Z)^*).
\]
Since $\FV$ is compact, we have the natural isomorphisms
\[
\FV(V_X\otimes V_Y,V^*_Z)\simeq \FV(V_X,V_Y^*\otimes V_Z^*),
\]
determined by the equalities
\[
\<f(x\otimes y),z\>=\<h(x),y\otimes z\>,\qquad x\in V_X,\ y\in V_Y,\ z\in V_Z,
\]
for $f\in \FV(V_X\otimes V_Y,V_Z^*)$ and $h\in \FV(V_Z,V_Y^*\otimes V_Z^*)$. Since
$A_{X\otimes Y}$ is an affine span of $A_X\otimes A_Y$, we see that
$f$ is in $\Af$ if and only if $f(x\otimes y)\in \tilde A_Z$ for all $x\in A_X$, $y\in
A_Y$, that is, 
\[
1=\<f(x\otimes y),z\>=\<h(x),y\otimes z\>\qquad \forall x\in A_X,\
\forall y\in A_Y,\ \forall z\in A_Z.
\]
But this is equivalent to
\[
h(x)\in (A_Y\otimes A_Z)^\sim=\tilde A_{Y\otimes Z},\qquad \forall x\in A_X,
\]
which means that $h\in \Af$.

\end{proof}

\subsubsection{The dual tensor product}

Let us define the dual tensor product by $\odot$, that is
\[
X\odot Y=(X^*\otimes Y^*)^*.
\]
We then have
\begin{align*}
L_{X\odot Y}&=S^\perp_{X^*\otimes Y^*}=(S_{X^*}\otimes S_{Y^*})^\perp=(L_X^\perp\otimes
L_Y^\perp)^\perp\\
S_{X\odot Y}&= L_{X^*\otimes Y^*}^\perp=(\tilde a_X\otimes
S_Y^\perp)^\perp\wedge(S_X^\perp\otimes \tilde a_Y)^\perp\wedge (S_X^\perp\otimes
S_Y^\perp)^\perp
\end{align*}
In particular,
\[
d_{X\odot Y}=D_Xd_Y+d_XD_Y-d_Xd_Y.
\]
\begin{lemma}\label{lemma:tensors} Let $X$, $Y$ be nontrivial. Then $X\otimes Y=X\odot Y$
exactly in one of the following situations:
\begin{enumerate}
\item $X\simeq I$ or $Y\simeq I$,
\item $d_X=d_Y=0$,
\item $D_X=d_X+1$ and $D_Y=d_Y+1$ (Objects with this property will be called
first order).
\end{enumerate}

\end{lemma}

\begin{proof} It is easy to see that (when identifying $X=X^{**}$), we have $A_X\otimes
A_Y\subseteq \tilde A_{X^*\otimes  Y^*}$, hence $A_{X\otimes Y}\subseteq A_{X\odot Y}$. We see from the above computatons that
\[
d_{X\odot Y}-d_{X\otimes Y}=d_X(D_Y-1)+(D_X-1)d_Y-2d_Xd_Y\ge 0,
\]
with equality if and only if the conditions of the lemma hold.

\end{proof}


\subsubsection{The no signaling product} 

\begin{lemma}\label{lemma:otimes_odot}
The space $A_{X\otimes Y}$ is precisely the affine subspace of elements $w\in A_{X\odot Y}$,
such that $\<w,\cdot \otimes \tilde a_Y\>$ and $\<w,\tilde a_X\otimes \cdot\>$ do not
depend on the choice of $\tilde a_Y\in \tilde A_Y$ and $\tilde a_X\in \tilde A_X$.
\end{lemma}

\begin{proof} Any element $w\in A_{X\otimes Y}$ has the form $w=\sum_i\alpha_i x_i\otimes
y_i$, for $x_i\in A_X$, $y_i\in A_Y$ and $\sum_i\alpha_i=1$. It follows that for any
$\tilde a_X\in \tilde A_X$ and $\tilde a_Y\in \tilde A_Y$,
\[
\<w,\cdot\otimes \tilde a_Y\>=\sum_i\alpha_ix_i,\qquad \<w,\tilde a_X\otimes
\cdot\>=\sum_i\alpha_iy_i.
\]
Conversely, assume that $w\in A_{X\odot Y}$ has this property, then for any $\tilde x\in
L_{X^*}$ and
$\tilde y\in L_{Y^*}$, we have
\[
\<w,\cdot\otimes \tilde y\>=0,\qquad \<w,\tilde x\otimes \cdot\>=0.
\]
It follows that
\begin{align*}
w&\in (V_X^*\otimes L_{Y^*})^\perp\cap (L_{X^*}\otimes V_Y^*)^\perp=
(V_X\otimes S_Y)\cap (S_X\otimes V_Y)=S_X\otimes S_Y
\end{align*}
Since $w\in A_{X\odot Y}$, we have $\<w,\tilde a_X\otimes \tilde a_Y\>=1$ for any choice
of $\tilde a_X\in \tilde A_X$,  $\tilde a_Y\in \tilde A_Y$. Since $\tilde a_X\otimes
\tilde a_Y\in \tilde A_{X\otimes Y}$ and $S_{X\otimes Y}=S_X\otimes S_Y$, this implies
$w\in A_{X\otimes Y}$.

\end{proof}


We will now define one-sided variants of this property. Namely, let 
\begin{align*}
A_{X\prec Y}&:=\{w\in A_{X\odot Y},\ \<w,\cdot \otimes \tilde a_Y\>\text{ does not depend on
} \tilde a_Y\in \tilde A_Y\}\\
A_{X\succ Y}&:=\{w\in A_{X\odot Y},\ \<w,\tilde a_X \otimes \cdot\>\text{ does not depend on
} \tilde a_X\in \tilde A_X\}.
\end{align*}
We then put $X\prec Y=(V_X\otimes V_Y, A_{X\prec Y})$ and $X\succ Y=(V_X\otimes V_Y,
A_{X\succ Y})$.

\begin{lemma}\label{lemma:prec} For any choice of $a_Y\in A_Y$, we have
\[
L_{X\prec Y}=V_X\otimes L_Y+L_X\otimes a_Y,\qquad S_{X\prec Y} =V_X\otimes L_Y+S_X\otimes
a_Y.
\]
Similarly, for any $a_X\in A_X$, we have
\[
L_{X\succ Y}=L_X\otimes V_Y+a_X\otimes L_Y,\qquad S_{X\succ Y} =L_X\otimes V_Y+a_X\otimes
S_Y.
\]
\end{lemma}

\begin{proof} By the definition, we have
\[
L_{X\prec Y}= L_{X\odot Y}\cap (V_X^*\otimes L_{Y^*})^\perp=(S_{X^*}\otimes
S_{Y^*})^\perp\cap (V_X\otimes S_Y)=V_X\otimes L_Y+L_X\otimes a_Y,
\]
for any element $a_Y\in A_Y$.
The proof for $\succ$ is similar.

\end{proof}




For the rest of this section, we fix some  $a_X\in A_X$ and $\tilde a_X\in \tilde A_X$. We will use the notation
$X_{\min}:=(V_X,\{a_X\})$ and 
$X_{\max}=(V_X, \{\tilde a_X\}^\sim)$. 

%We then have the diagram
%\[
%\xymatrix{
% & & X\prec Y \ar[rd] \\
%X_{\min}\otimes Y_{\min} \ar[r] &X\otimes Y \ar[ru] \ar[rd] &  & X\odot Y
%\ar[r] & X_{\max}\otimes Y_{\max}\\
% &  & X\succ Y \ar[ru]
%}
%\]
%where the arrows are given by identity maps.
%
We also introduce a decomposition of $V_X$ into an independent family of subspaces
$L_X^0,L^1_X,L^2_X$ as
$L_X^0:=\mathbb Ra_X$, $L_X^1:=L_X$ and $L_X^2$ is any complement of $L_X$ in the subspace
$\{\tilde a_X\}^\perp$. We see that the $L$ or $S$ spaces of any of the objects discussed
in this paragraph is a union of some of the subspaces $L_X^i\otimes L_Y^j$, $i,j=0,1,2$. 
We may therefore represent the subspaces in question by $3\times 3$ matrices such that 
the $i,j$-th element is 1 if the subspace contains $L_X^i\otimes L_Y^j$ and 0 otherwise.
For example, we have
\begin{equation}\label{eq:matrices}
L_{X\otimes Y}\equiv \begin{bmatrix} 0& 1&0\\ 1 &1 &0\\ 0 & 0&0\end{bmatrix}, \ 
L_{X\odot Y}\equiv \begin{bmatrix} 0& 1&0\\ 1 &1 &1\\ 0 & 1&0\end{bmatrix},\ 
L_{X\prec Y}\equiv \begin{bmatrix} 0& 1&0\\ 1 &1 &0\\ 0 & 1 &0\end{bmatrix}, \ 
L_{X\succ Y}\equiv \begin{bmatrix} 0& 1&0\\ 1 &1 &1\\ 0 & 0&0\end{bmatrix}.
\end{equation}
The $S$-spaces can be obtained from these by putting the top left  element to 1. Notice
also that all these objects belong to the set of objects $Z=(V_X\otimes V_Y, A_Z)$ such
that
\[
X_{\min}\otimes Y_{\min}\hookrightarrow  Z \hookrightarrow X_{\max}\otimes
Y_{\max}(=X_{\max}\odot Y_{\max})
\]
and this set forms a lattice under inclusion ordering with $Z_0\wedge Z_1=Z_0\sqcap Z_1$,
$Z_0\vee Z_1=Z_0\sqcup Z_1$, where $\sqcap$ and $\sqcup$ are the pulback and pushout 
of the inclusions $X_{\min}\otimes Y_{\min}\hookrightarrow Z_i \hookrightarrow
X_{\max}\otimes Y_{\max}$. Furthermore, since $\{L_X^i\otimes L_Y^j\}$ is an independent
decomposition of $V_X\otimes V_Y$, all the objects  in \eqref{eq:matrices} are contained in a
distributive sublattice of objects such that $A_Z=a_X\otimes a_Y+L$, where $L$ is a subspace
represented by a  matrix $M_Z$ with the top left element equal to 0.
For such elements $Z_1$ and $Z_2$, the representing matrices  $M_{Z_1\sqcap Z_2}$ resp.
$M_{Z_1\sqcup Z_2}$ are given by
poinwise minimum resp. maximum of $M_{Z_1}$ and $M_{Z_2}$.


Some further useful elements of this sublattice are represented as
\[
L_{X_{\max}\otimes Y}\equiv\begin{bmatrix}0 & 1 & 0\\ 1 & 1& 0\\ 1& 1&0  \end{bmatrix},\ 
L_{X\otimes Y_{\max}}\equiv\begin{bmatrix}0 & 1 & 1\\ 1 & 1& 1\\ 0& 0&0  \end{bmatrix},\ 
L_{X_{\min}\odot Y}\equiv\begin{bmatrix}0 & 1 & 0\\ 0 & 1& 0\\ 0& 1&0  \end{bmatrix},\ 
L_{X\odot Y_{\min }}\equiv\begin{bmatrix}0 & 0 & 0\\ 1 & 1& 1\\ 0& 0&0  \end{bmatrix}. 
\]
From these consideration, the following is immediate.

\begin{lemma}\label{lemma:lattice} We have
\begin{align*}
X\prec Y &= (X\otimes Y) \sqcup (X_{\min}\odot Y)=(X\odot Y)\sqcap (X_{\max}\otimes Y)\\
X\succ Y &= (X\otimes Y) \sqcup (X\odot Y_{\min})=(X\odot Y)\sqcap (X\otimes Y_{\max})\\
X\otimes Y & = (X\prec Y)\sqcap (X\succ Y)\\
X\odot Y & = (X\prec Y)\sqcup (X\succ Y).
\end{align*}


\end{lemma}









We have 
the inclusions 
\[
X_a\to X\to X^{\tilde a}.
\]
We also fix $b\in A_Y$, $\tilde b\in \tilde A_Y$. By inclusions, we have the following diagrams
\[
X_a\otimes Y_b\to X\otimes Y,\qquad X_a\otimes Y_b\to  X_a\odot Y
\]
and
\[
X\odot Y\to X^{\tilde a}\odot Y^{\tilde b}=X^{\tilde
a}\otimes Y^{\tilde b},\qquad X\otimes Y^{\tilde b}\to X^{\tilde a}\otimes Y^{\tilde b}.
\]


\begin{lemma}\label{lemma:minmax}
$X\prec Y=X\otimes Y\sqcup X\odot Y_b=X\odot Y \sqcap X\otimes Y^{\tilde b}$.
\end{lemma}


We see that  the identity map $id_{V_X\otimes V_Y}$ defines bimorphisms
\[
X\otimes Y \to X\prec Y\to X\odot Y,\qquad X\otimes Y\to X\succ Y\to X\odot Y.
\]

\begin{lemma}\label{lemma:precsucc_pushpul} The  pushout and pullback of the above
diagram are
\[
X\otimes Y=(X\prec Y)\sqcap (X\succ Y),\qquad X\odot Y= (X\prec Y)\sqcup (X\succ Y).
\]

\end{lemma}

\begin{proof}  We have by Lemma \ref{lemma:otimes_odot} that 
\[
A_{X\otimes Y}=A_{X\prec Y}\cap A_{X\succ Y}=A_{(X\prec Y)\sqcap (X\succ Y)},
\]
we clearly have the last equality since the intersection $A_{X\prec Y}\cap A_{X\succ Y}$
is nonempty. For the second part,   


\end{proof}





To each object $X=(V_X,A_X,a_X,\tilde a_X)$ we may define two object
\[
X_{\min}:=(V_X,\{a_X\},a_X,\tilde a_X),\qquad X_{\max}:=(V_X,\{\tilde a_X\}^\sim,a_X,\tilde a_X). 
\]
It is easily seen that $X_{\min}=(X^*_{\max})^*$ and $X_{\max}=(X^*_{\min})^*$, moreover,
$X_{\max}$ and $(X_{\min})^*$ are first order objects. We have the inclusions
\[
X_{\min}\xrightarrow{id} X\xrightarrow{id} X_{\max}.
\]
We also have the inclusions
\[
X\otimes Y\to X\odot Y \to X_{\max}\odot Y_{\max}=X_{\max}\otimes Y_{\max}
\]
and
\[
X\otimes Y \to X_{\max}\otimes Y\to X_{\max}\otimes Y_{\max}, \quad X\otimes Y \to X\otimes Y_{\max}\to X_{\max}\otimes Y_{\max}.
\]
We can therefore define pullbacks and pushouts,  which then becomes
\[
(X_{\max}\otimes Y)\sqcap (X\otimes Y_{\max})=X\otimes Y,\qquad (X_{\max}\otimes Y)\sqcup
(X\otimes Y_{\max})=X_{\max}\otimes Y_{\max}.
\]
Hence we may decompose $X\odot Y$ into two parts
\[
X\prec Y:= (X\odot Y)\sqcap (X_{\max}\otimes Y),\qquad X\succ Y:=(X\odot Y) \sqcap
(X\otimes  Y_{\max}).
\]



Note that these forms do not depend on the choice of the elements $a_X,a_Y$...!

\begin{lemma}\label{lemma:decomp} We have
\[
X\otimes Y=(X\prec Y) \sqcap (X\succ Y),\qquad X\odot Y= (X\prec Y)\sqcup (X\succ Y).
\]

\end{lemma}

\begin{proof} We have 

\begin{align*}
(X\prec Y) \sqcap (X\succ Y)&=((X\odot Y)\sqcap (X_{\max}\otimes Y))\sqcap ((X\odot
Y)\sqcap (X\otimes Y_{\max}))\\
&= (X\odot Y) \sqcap((X_{\max}\otimes Y)\sqcap (X\otimes Y_{\max}))=(X\odot Y)\sqcap
(X\otimes Y)=X\otimes Y.
\end{align*}
The second equality follows easily from Lemma \ref{lemma:prec}
\end{proof}

We next show that $-\prec -$ and $-\succ -$ define a functor $\Af\times \Af\to \Af$. Let
$X_1\xrightarrow{f} Y_1$ and $X_2\xrightarrow{g} Y_2$, we will show that 
$X_1\prec Y_1\xrightarrow{f\otimes g} X_2\prec Y_2$. For this, we need to prove that 
$(f\otimes g)(A_{X_1\prec X_2})\subseteq A_{X_2\prec Y_2}$ and $(f\otimes g)(A_{X_1\succ
X_2})\subseteq A_{X_2\succ Y_2}$. This is clear from Lemma \ref{lemma:prec}. 



\begin{lemma}\label{lemma:precmonoidal} $(\Af,\prec,I)$ is a monoidal category.  

\end{lemma}

\begin{proof} It is easily checked from Lemma \ref{lemma:prec} that
$\alpha_{X,Y,X}(L_{(X\prec Y)\prec Z})=L_{X\prec(Y\prec Z)}$ and clearly also
$\alpha_{X,Y,Z}(a_X\otimes a_Y\otimes a_Z)=a_X\otimes a_Y\otimes a_Z$, so that $\alpha$ is
the associator. Since $I\otimes X=I\odot X$ and $X\odot I=X\otimes I$, we have 
$I\prec X=I\otimes X$ and $X\prec I=X\otimes I$, so $\lambda$ and $\rho$ are the
unitors. But note that $\sigma_{X,Y}(A_{X\prec Y})=A_{Y\succ X}$, so this structure is
not symmetric. 

\end{proof}

We have $(X\prec Y)^*=X^*\prec Y^*$. Indeed, by duality,
\begin{align*}
(X\prec Y)^*&=((X\odot Y)\sqcap (X_{\max}\odot Y))^*=(X\odot Y)^*\sqcup (X_{\max}\otimes
Y)^*\\
&= (X^*\otimes Y^*)\sqcup (X_{\max}^*\odot Y^*)
\end{align*}




\subsubsection{Internal hom}

The internal hom has the form
\begin{equation}\label{eq:ihom}
[X,Y]=(X\otimes Y^*)^*=X^*\odot Y.
\end{equation}
We then have 
\begin{align*}
L_{[X,Y]}&=(S_X\otimes L_Y^\perp)^\perp= (V_X^*\otimes L_Y)\vee (L_{X^*}\otimes V_Y), \\
S_{[X,Y]}&=(\tilde a_X\otimes
S_Y^\perp)^\perp\wedge(L_X\otimes \tilde a_Y)^\perp\wedge (L_X\otimes
S_Y^\perp)^\perp=(V_X^*\otimes L_Y)\vee (L_{X^*}\otimes V_Y)\vee (\tilde a_X\otimes a_Y).
\end{align*}
and
\[
d_{[X,Y]}=D_XD_Y-(d_X+1)(D_Y-d_Y).
\]


As we have seen in $\FV$, the space $V_{[X,Y]}=V_X^*\otimes V_Y$ is identified with the
space of all linear maps $V_X\to V_Y$, by \eqref{eq:fvhoms}. We will show that $A_{[X,Y]}$ corresponds to the
affine subspace of maps mapping $A_X$ into $A_Y$, that is, morphisms in $\Af$. Indeed, we see from \eqref{eq:fvhoms}
that $f$ is in $\Af$ if and only if 
\[
\<f(x),y^*\>=\<w,x\otimes y^*\>=1, \qquad x\in A_X,\ y^*\in \tilde A_Y,
\]
which is equivalent to $w\in (A_X\otimes \tilde A_Y)^\sim=\tilde A_{X\otimes Y^*}$. 

\subsubsection{The no signaling product}

For two objects $X$, $Y$ we define 
\[
X\prec Y :=(V_X\otimes V_Y, A_{X\prec Y},a_X\otimes a_Y,\tilde a_X\otimes \tilde a_Y),
\]
where $A_{X\prec Y}$ is determined by
\begin{align*}
S_{X\prec Y}=V_X\otimes S_Y\cap S_{X\odot Y}=(V_X\otimes S_Y)\cap (L_{X\odot Y}\vee
\{a_X\otimes a_Y\})=(V_X\otimes S_Y)\cap((V_X\otimes L_Y)\vee (L_X\otimes V_Y)\vee
\{a_X\otimes a_Y\}).
\end{align*}


\begin{lemma}\label{lemma:}


\end{lemma}

We may similarly define $X\succ Y$. Setting $f\prec g=f\otimes g$ for $X_1\xrightarrow{f}
X_2$, $Y_1\xrightarrow{g} Y_2$, we see that $(-\prec -)$ is functorial. Indeed, to show
that $X_1\prec Y_1\xrightarrow{f\otimes g} X_2\prec Y_2$, we need to
show that $f\otimes g(A_{X_1\prec Y_1})\subseteq A_{X_2\prec Y_2}$. Assume $w\in
A_{X_1\prec Y_1}$, that is, $w\in V_{X_1}\otimes S_{Y_1}$ and $\<w,\tilde a_{X_1}\otimes
\tilde a_{Y_1}\>=1$. 

\subsubsection{Dualizable (nuclear) objects}

An object in $\Af$ is nuclear if the natural map $X^*\otimes X\to [X,X]$ is an isomorphism
(santocanale). That is, the inclusion $X^*\otimes X\subseteq X^*\odot X$ that comes from the embedding 
\[
\tilde A_X\otimes A_X\subseteq (A_X\otimes \tilde A_X)^\sim
\]
becomes an equality. As we have seen in Lemma \ref{lemma:tensors}, for proper objects we
have $X^*\otimes X=X^*\odot X$ if and only if
\[
d_X+1=D_X=D_{X^*}=d_{X^*}+1=D_X-d_X.
\]
It follows that $d_X=0$ and $D_X=1$, so that $X\simeq I$. Hence the tensor unit is the
unique dualizable (or nuclear) object in $\Af$.


\subsubsection{No signaling}

We say that $X\xrightarrow{f} Y$ is no signaling if
\[
y^*\circ f=\tilde a_Y\circ f,\qquad \forall y\in Y^*=[Y,I],
\]
in other words
\[
y\circ f=0,\qquad \forall y^*\in L_{Y^*}=S_Y^\perp.
\]
Taking $w\in A_{[X,Y]}$ be the corresponding elements, this means that
\[
\<w,x\otimes y^*\>=0,\qquad \forall x\in V_X,\ y^*\in S_Y^\perp,
\]
in other words
\[
w\in (V_X\otimes S_Y^\perp)^\perp=V^*_X\otimes S_Y,
\]
so that
\[
w\in A_{[X,Y]}\cap (V^*_X\otimes S_Y).
\]
Since $a_{[X,Y]}=\tilde a_X\otimes a_Y\in V^*_X\otimes S_Y$, we have that
\[
a_{[X,Y]}-w\in L_{[X,Y]}\cap V^*_X\otimes S_Y=(S_X\otimes L_Y^\perp)^\perp\cap
V^*_X\otimes S_Y=(V_X^*\otimes L_Y)+ (L_{X^*}\otimes a_Y).
\]
We can also define no signaling in the oposite way, that is,
\[
f(x)=f(a_X),\qquad \forall x\in A_X.
\]
This is of course the same as 
\[
f(x)=0,\qquad \forall x\in L_X,
\]
or
\[
\<w,x\otimes y^*\>=0,\qquad \forall x\in L_X,\ y^*\in V_Y^*,
\]
that is,
\[
w\in (L_X\otimes V_Y^*)^\perp=L_X^\perp\otimes V_Y=S_{X^*}\otimes V_Y.
\]
It follows that
\[
\tilde a_X\otimes a_Y-w\in L_{[X,Y]}\cap S_{X^*}\otimes V_Y=L_{X^*}\otimes V_Y+\tilde
a_X\otimes L_Y.
\]

\subsection{Once more on the monoidal structures}

\subsubsection{Tensor product}

We have
\[
L_{X\otimes Y}=(a_X\otimes L_Y)+(L_X\otimes a_Y)+(L_X\otimes L_Y)=(S_X\otimes
L_Y)+(L_X\otimes a_Y)=(L_X\otimes S_Y)+(a_X\otimes L_Y)
\]
A closed symmetric monoidal structure. We have 
\[
L_{X_{\max} \otimes Y}=V_X\otimes L_Y+\{\tilde a_X\}^\perp\otimes a_Y,\qquad L_{X_{\min}\otimes Y}=a_X\otimes L_Y.
\]
\begin{lemma}\label{lemma:maxtensor}
We have
\[
X\otimes Y=(X_{\max}\otimes Y)\sqcap (X\otimes Y_{\max}). 
\]

\begin{proof} This is easy, since
\[
S_{X_{\max}\otimes Y}\cap S_{X\otimes Y_{\max}}=(V_X\otimes S_Y)\cap (S_X\otimes
V_Y)=S_X\otimes S_Y.
\]

\end{proof}

\end{lemma}

\subsubsection{Dual product}
By definition,  $X\odot Y=(X^*\otimes Y^*)^*$. We have
\[
L_{X\odot Y}=(L_X^\perp\otimes L_Y^\perp)^\perp=(V_X\otimes L_Y)\vee (L_X\otimes V_Y).
\]
We have
\[
L_{X_{\max}\odot Y}=(V_X\otimes L_Y)\vee(\{\tilde a_X\}^\perp\otimes V_Y),\qquad
L_{X_{\min}\odot Y}=V_X\otimes L_Y.
\]
\begin{lemma}\label{lemma:maxdual} We have
\begin{align*}
X_{\max}\otimes Y_{\max}&=(X_{\max}\odot Y)\sqcup (X\odot Y_{\max})\\
X\odot Y&=(X_{\min}\odot Y)\sqcup (X\odot Y_{\min})\\
X\otimes Y&= (X_{\min}\otimes Y)\sqcup (X\otimes Y_{\min})\sqcup (X_{\min}\odot Y \sqcap
X\odot Y_{\min}) 
\end{align*}


\end{lemma}

\begin{proof} The first is easy, the seconf follows from Lemma \ref{lemma:maxtensor} by
duality, the third is also easy.

\end{proof}

\subsection{The no signalling product}

Let us define $X\prec Y:= (X\odot Y)\sqcap (X_{\max}\otimes Y)$. We have
\[
L_{X\prec Y}=V_X\otimes L_Y+L_X\otimes a_Y=L_{X_{\min}\odot Y}+L_{Y\otimes Y_{\min}}.
\]
So that
\[
X\prec Y:= (X\odot Y)\sqcap (X_{\max}\otimes Y)=(X_{\min}\odot Y)+(X\otimes Y_{\min})
\]

\begin{lemma}\label{lemma:nosig}
We have
\begin{align*}
(X\otimes Y)\sqcup (X_{\min}\odot Y)&=(X\odot Y)\sqcap (X_{\max}\otimes Y)\\
=(X_{\min}\odot Y) + (X\otimes Y_{\min})&=(X_{\max}\otimes Y)\sqcap (X\odot Y_{\max}).
\end{align*}
Let us denote the above object by $X\prec Y$. Then $A_{X\prec Y}$ is the set of elements
in $V_X\otimes V_Y$ such that $\<w,\cdot \otimes y^*\>$ is a fixed element in $A_X$,
independently of $y^*\in \tilde A_Y$.
\end{lemma}

Blbe uvedenie, definicia!

\begin{proof} We see that $A_{X\prec Y}\subseteq A_{X\odot Y}$, moreover,
\[
A_{X\prec Y}=\{w\in A_{X\odot Y},\ \<w,id_X\otimes y^*\>=0,\ \forall y^*\in L_{Y^*}\}.
\]
In other words, since clearly $a_X\otimes a_Y\in A_{X\prec Y}$,
\begin{align*}
L_{X\prec Y}&=\{w-a_X\otimes a_Y,\ w\in A_{X\prec Y}\}=L_{X\odot Y}\cap (V^*_X\otimes
L_Y^*)^\perp=(L_X^\perp\otimes S_{Y^*})^\perp\cap(V_X^*\otimes L_{Y^*})^\perp\\
&=((L_X^\perp\otimes S_{Y^*})\vee (V_X^*\otimes L_{Y^*}))^\perp=((V_X^*\otimes
L_{Y^*})+(S_X^*\otimes \tilde a_Y))^\perp=S_{(X\prec Y)^*}^\perp
\end{align*}
But also
\begin{align*}
L_{X\odot Y}\cap (V^*_X\otimes
L_Y^*)^\perp&=((V_X\otimes L_Y)\vee L_X\otimes V_Y)\cap (V_X\otimes S_Y)\\
&=
((V_X\otimes L_Y)+(L_X\otimes a_Y)+(L_X\otimes S_Y'))\cap ((V_X\otimes L_Y)+(L_X\otimes
a_Y)+ (L_X'\otimes a_Y))\\
&=((V_X\otimes L_Y)+(L_X\otimes a_Y). 
\end{align*}

First note that we have 
\[
L_{X_{\min}\odot Y}=V_X\otimes L_Y,\qquad L_{X\otimes Y_{\min}}=L_X\otimes a_Y
\]
and therefore
\[
L_{X\otimes Y_{\min}}\cap L_{X_{\min}\odot Y}=\{0\}.
\]
Further,
\[
L_{X\otimes Y}= (S_X\otimes L_Y)+ (L_X\otimes a_Y)=(S_X\otimes L_Y)+L_{X\otimes Y_{\min}}
\]
and
\[
L_{X\odot Y}=(V_X\otimes L_Y)\vee (L_X\otimes V_Y),\qquad L_{X_{\max}\otimes Y}=(V_X\otimes
L_Y)+(\{\tilde a_X\}^\perp\otimes a_Y)
\]
We have
\[
S_{(X\otimes Y)\sqcup (X_{\min}\odot Y)}=S_{X\otimes Y}\vee S_{X_{\min}\odot Y}=
S_{X\otimes Y}\vee L_{X_{\min}\odot Y}
\]

\end{proof}

\subsection{The category $\Afh$} 


The category $\Afh$ will be constructed as a subcategory in $\Af$. 

\subsubsection{First order objects}

It is easily seen that the following are equivalent:
\begin{enumerate}
\item $D_X=d_X+1$;
\item $S_X=V_X$;
\item $L_X=\{\tilde a_X\}^\perp$;
\item $S_{X^*}=\mathbb R \tilde a_X$;
\item $L_{X^*}=\{0\}$.
\end{enumerate}
We say that an object $X$ is first order if any of these conditions is fulfilled. We have
seen that for proper objects, $X\otimes Y=X\odot Y$ if and only if both $X$ and $Y$ are
first order. We also have

\begin{lemma}\label{lemma:firstorder} $X$ is first order if and only if  $X\otimes
X=X\odot X$.

\end{lemma}
`
\begin{lemma}\label{lemma:1ordertensor} Let $X$, $Y$ be first order, then $X\otimes Y$ is
first order.

\end{lemma}

\begin{proof} We have
\[
S_{X\otimes Y}=S_X\otimes S_Y=V_X\otimes V_Y=V_{X\otimes Y}.
\]

\end{proof}


\subsubsection{Channels}
A channel is an object $[X,Y]$ where  $X$ and $Y$ are first order. As we have seen,
\[
X^*\otimes Y\subseteq X^*\odot Y=[X,Y].
\]
If $X$ is first order, $\tilde A_X=\{\tilde a_X\}$ and the elements of $A_{X^*\otimes
Y}=\tilde a_X\otimes A_Y$ are identified with channels of the form
\[
f(x)=\<\tilde a_X,x\>y,\qquad x\in V_X,
\]
for some $y\in A_Y$. Such maps will be called replacement channels.

\begin{lemma}\label{lemma:channels} Let $X$, $Y$ be first order and let  $w\in V_X^*\otimes V_Y$. Then $w
\in A_{[X,Y]}$ if and only if
\[
\circ_Y :w_{X^*Y}\otimes \tilde a_Y\mapsto \tilde a_X.
\]
\end{lemma}

\begin{proof} Let $f:V_X\to V_Y$ be the map corresponding to $w$, then 
\[
\circ_Y(w\otimes \tilde a_Y)=(V_X^*\otimes e_{V_Y})(w\otimes \tilde a_Y)=\tilde a_Y\circ
f,
\]
where $\tilde a_Y\in V_Y^*$ is seen as a map $V_y\to \mathbb R$. So $\tilde a_Y\circ f:
V_X\to \mathbb R$ is an element in $V_X^*$. We know that $w\in A_{[X,Y]}$ iff
$f(A_X)\subseteq A_Y$, which is equivalent to  $\tilde a_Y\circ f(x)=1$ for all $x\in A_X$, so
that $\tilde a_Y\circ f\in \tilde A_X=\{\tilde a_X\}$, since $X$ is first order.  
\end{proof}

\begin{lemma}\label{lemma:mapsdual} Let $Y$ be first order and $w\in V_X^*\otimes V_Y$.
Then $w\in A_{[X,Y]}$ if and only if
\[
\circ_Y(w_{X^*Y}\otimes \tilde a_Y)\in \tilde A_X.
\]
Moreover, 
\[
\tilde A_{[X,Y]}=A_X\otimes \{\tilde a_Y\}.
\]


\end{lemma}

\begin{proof} Since $Y$ is first order, we have $A_{Y^*}=\tilde A_Y=\{\tilde a_Y\}$ and by
\eqref{eq:ihom}
\[
\tilde A_{[X,Y]}=A_{X\otimes Y^*}=A_X\otimes \{\tilde a_Y\}.
\]
As in the above proof, let $f:V_X\to V_Y$ be the map corresponding to $w$. Then $\tilde
a_Y\circ f\in V_X^*$ and $w\in A_{[X,Y]}$ iff $f(A_X)\subseteq A_Y$. This means that
\[
\tilde a_Y\circ f(x)=1,\qquad \forall x\in A_X,
\]
which means that $\tilde a_Y\circ f\in \tilde A_X$.

\end{proof}

\subsubsection{$\Afh$}

The category $\Afh$ is the full subcategory in $\Af$ created from first order objects by
taking tensor products and duals. We will add more later. We will use the notation
$V_{XY^*}$ for $V_X\otimes V^*_Y$, etc. 

Any object $X$ in $\Afh$ is created from first order objects $X_1,\dots, X_k$, so that
$V_X=\tilde V_{X_1}\otimes\dots\otimes \tilde V_{X_k}$, where $\tilde V_{X_i}$ is either
$V_{X_i}$ or $V^*_{X_i}$, $i=1,\dots,k$. We will next show that any object is a set of
channels that contains all replacement channels. 



\begin{prop}\label{prop:afh} Let $X$ be an object in $\Afh$. Then there are  first order
objects $Y_I$ and $Y_O$ and inclusions $f$, $g$ such that
\begin{equation}\label{eq:inclusions}
Y_I^*\otimes Y_O \xrightarrow{f} X\xrightarrow{g} [Y_I,Y_O].
\end{equation}


\end{prop}

\begin{proof} Let $X$ be first order, then since $I$ is first order,
\[
I^*\otimes X=I\otimes X \xrightarrow{\lambda_X} X\xrightarrow{\lambda^{-1}_X} I\otimes
X=I\odot X=[I,X].
\]
Clearly, $f=\lambda_X$ and $g=\lambda^{-1}_X$ are inclusions. Now assume that $Z$
satisfies \eqref{eq:inclusions} and let $X=Z^*$. Taking duals and composing with
symmetries, we get
\[
Y_O^*\otimes Y_I\xrightarrow{\sigma_{V_{Y,O}^*,V_{Y_I}}} Y_I\otimes Y_0^*=[Y_I\otimes
Y_O]^*\xrightarrow{g^*} X\xrightarrow{f^*} (Y_I^*\otimes
Y_O)^*\xrightarrow{\sigma_{V_{Y_I},V_{X_O}^*}} (Y_O\otimes Y_I)^*=[Y_O,Y_I].
\]
Since the compositions of $f^*$ and $g^*$ with symmetries are inclusions, we see that $X$
satisfies \eqref{eq:inclusions}.

Next, let $X_1$ and $X_2$ satisfy \eqref{eq:inclusions}  with some first order objects $Y_I^i$, $Y_O^i$ and
inclusions $f^i,g^i$, $i=1,2$, and let $X=X_1\otimes X_2$. We then have, using the
appropriate symmetries
\[
Y_I^1Y_I^2\otimes (Y_O^1Y_O^2)^*\xrightarrow{\sigma_{Y_I^2,Y_O^1}} Y_I^1\otimes
(Y_O^1)^*\otimes Y_I^2\otimes (Y_O^1)^*\xrightarrow{f^1\otimes f^2} X
\xrightarrow{g^1\otimes g^2} [Y_I^1,Y_O^1]\otimes
[Y_I^2,Y_O^2]\xrightarrow{\sigma_{Y_O^1,Y_O^2}}[Y_I^1Y_I^2,I_O^1Y_O^2].
\]
Perhaps the last arrow needs some checking, so lt us do it properly. We need to show that
for $w\in A_{[Y_I^1,Y_O^1]\otimes
[Y_I^2,Y_O^2]}$, we have $\sigma_{Y_O^1,Y_O^2}(w)\in A_{[Y_I^1Y_I^2,I_O^1Y_O^2]}$, but
this is clear using Lemma \ref{lemma:channels}.

\end{proof}

The pair $(Y_I,Y_O)$ for an object $X$ will be called the $\type$ of $X$. For objects of
the same $\type$ we may take
pullbacks and pushouts of the  corresponding inclusions.




Pullbacks are intersections, pushouts the affine mixture.

Channels into (from) products and coproducts

We define $\Afh$ as the full subcategory of $\Af$ containing all first order objects and
closed under (finite products,) duals and  tensor products . 



\end{document}

